\documentclass[letterpaper, 10 pt, journal, twoside]{IEEEtran}

\IEEEoverridecommandlockouts %


\markboth{IEEE Robotics and Automation Letters. Preprint Version. Accepted June, 2020}
{Lusk \MakeLowercase{\textit{et al.}}: A Distributed Pipeline for Scalable, Deconflicted Formation Flying} 


\input{macros.tex}
\pdfminorversion=4

\newcommand{\edittwo}[1]{\textcolor{black}{#1}}
\newcommand{\edit}[1]{\textcolor{black}{#1}}

\title{%
	 A Distributed Pipeline for \\ Scalable, Deconflicted Formation Flying
	}

\author{Parker C. Lusk, Xiaoyi Cai, Samir Wadhwania, Aleix Paris, Kaveh Fathian, Jonathan P. How%
    \thanks{Manuscript received: February 24, 2020; Revised: May 20, 2020; Accepted: June 1, 2020}%
	\thanks{
	    This paper was recommended for publication by N.Y.\ Chong upon evaluation of the Associate Editor and Reviewers' comments. %
	    Research supported in part by NASA Convergent Aeronautics Solutions project Design Environment for Novel Vertical Lift Vehicles (DELIVER),
		ARL DCIST under Cooperative Agreement Number W911NF-17-2-0181,
		and Boeing Research \& Technology.
		Computation support provided by Amazon Web Services.}
	\thanks{P.\ C.\ Lusk, X.\ Cai, S.\ Wadhwania, A.\ Paris,  K.\ Fathian and J.\ P.\ How are with the Department of Aeronautics and Astronautics, Massachusetts Institute of Technology.
	    {\{plusk, xyc, samirw, aleix, kavehf, jhow\}@mit.edu.}}
	\thanks{Digital Object Identifier (DOI): see top of this page.} %
}%

\begin{document}

\maketitle


\begin{abstract}
Reliance on external localization infrastructure and centralized coordination are main limiting factors for formation flying of vehicles in large numbers and in unprepared environments.
While solutions using onboard localization address the dependency on external infrastructure, the associated coordination strategies typically lack collision avoidance and scalability.
To address these shortcomings, we present a unified pipeline with onboard localization and a distributed, collision-free formation control strategy that scales to a large number of vehicles.
Since distributed collision avoidance strategies are known to result in gridlock, we also present a \edit{distributed} task assignment solution to deconflict vehicles.
We experimentally validate our pipeline in simulation and hardware.
The results show that our approach for solving the optimization problem associated with formation control gives solutions within seconds in cases where general purpose solvers fail due to high complexity.
In addition, our lightweight assignment strategy leads to successful and quicker formation convergence in
\SIrange[range-units=single,range-phrase=--]{96}{100}{\percent} of all trials,
whereas indefinite gridlocks occur without it for \SIrange[range-units=single,range-phrase=--]{33}{50}{\percent} of trials.
By enabling large-scale, deconflicted coordination, this pipeline should help pave the way for anytime, anywhere deployment of aerial swarms.
\end{abstract}


\begin{IEEEkeywords}
Swarms; Distributed Robot Systems; Multi-Robot Systems
\end{IEEEkeywords}
\vspace{-0.8em}


 \section*{Supplementary Material}


Video and open-source implementation available at \href{https://github.com/mit-acl/aclswarm}{\texttt{https://github.com/mit-acl/aclswarm}}.

\section{Introduction}\label{sec:intro}
\input{introduction.tex}




\input{overview.tex}


\input{motionplanning.tex}
\input{assignment.tex}


\input{experiments.tex}


\section{Conclusion and Future Work} 
\input{conclusion.tex}






\balance %

\bibliographystyle{IEEEtran}
\bibliography{Bibs}

\appendix \label{sec:Appendix}
\input{appendix.tex}

\end{document}
