\documentclass[letterpaper, 10 pt, conference]{formatting/ieeeconf}
\IEEEoverridecommandlockouts                              % This command is only needed if 
                                                            % you want to use the \thanks command
\overrideIEEEmargins                                      % Needed to meet printer requirements.
\pdfminorversion=4			% ICRA standard
\let\labelindent\relax
\usepackage{amsfonts}       % An extended set of fonts for use in mathematics
\let\proof\relax
\let\endproof\relax
\usepackage{amsthm}
\usepackage{wrapfig}
\usepackage{mathtools}      % Loads amsmath
\usepackage{amssymb}        % provides AMS fonts and symbols ex. \mathbb{...}
\usepackage{filecontents}
\usepackage{graphicx}       % enhanced support for graphics
\usepackage{marginnote}     % Add notes
\usepackage{marvosym}       % mvat
\usepackage{overpic}        % Add text on figures
\usepackage{tabularx}
\usepackage{cite}
\usepackage{color}
\usepackage[linesnumbered,algoruled,boxed,lined]{algorithm2e}
\usepackage[normalem]{ulem}
\usepackage{epstopdf}
% \usepackage[section]{placeins}
\usepackage{float}
\usepackage{enumitem}
\usepackage[normalem]{ulem}
\usepackage{lipsum}
\usepackage[a-2b,mathxmp]{pdfx}[2018/12/22]

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%% Side comments   %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifdraft
\draftfalse

\ifdraft
\usepackage[paperheight=11in,paperwidth=9.5in,
			left=1.25in,right=1.25in,
			top=0.75in,bottom=0.75in,
			heightrounded,marginparwidth=1.2in,
			marginparsep=0.05in]{geometry}
\usepackage{xcolor}
\usepackage{xargs} 
\usepackage[textsize=footnotesize]{todonotes}
\newcommandx{\nt}[2][1=]{\todo[linecolor=red,
			backgroundcolor=red!10,bordercolor=red,#1]{ #2}}
\newcommandx{\jy}[2][1=]{\todo[linecolor=green,
			backgroundcolor=green!10,bordercolor=green,#1]{JY: #2}}
\else
\newcommand{\nt}[1]{{}}
\newcommand{\jy}[1]{{}}
\fi

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Spacing related commands.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\iftwocolumn
\twocolumntrue

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Spacing related commands.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Space between figure and caption
%\setlength{\abovecaptionskip}{2pt}
%\setlength{\belowcaptionskip}{2pt}

% Space between text and figs
%\setlength{\dbltextfloatsep}{1.5pt plus .5pt minus .5pt}
%\setlength{\textfloatsep}{.15pt plus .5pt minus .5pt}
%\setlength{\intextsep}{1.5pt plus .5pt minus .5pt}

% Space between equations and text
%\setlength{\belowdisplayskip}{1pt} \setlength{\belowdisplayshortskip}{1pt}
%\setlength{\abovedisplayskip}{1pt} \setlength{\abovedisplayshortskip}{1pt}

% Paragraph formatting 
\setlength{\parskip}{1.5pt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Environments and Theorems
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newtheorem{problem}{Problem}
\newtheorem{proposition}{Proposition}[section]
\newtheorem{lemma}{Lemma}[section]
\newtheorem{observation}{Observation}[section]
\newtheorem{corollary}{Corollary}[section]
\newtheorem{theorem}{Theorem}[section]
\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]
\theoremstyle{remark}
\newtheorem*{remark}{Remark}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Algorithm2e setup
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\SetKwProg{Fn}{Function}{}{}
\SetKwComment{Comment}{$\triangleright$\ }{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Edits
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\changed}[1]{\textcolor{black}{#1}}
\def\ch#1#2{\sout{#1}\,\textcolor{blue}{#2}}
\newcommand{\JY}[1]{\textcolor{red}{JY: #1}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Adjusted indentation of subsubsections
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\makeatletter
\def\subsubsection{\@startsection{subsubsection}% name
                                 {3}% level
                                 {\z@ \hspace*{1mm}}% indent (formerly \parindent)
                                 {0ex plus 0.1ex minus 0.1ex}% before skip
                                 {0ex}% after skip
                                 {\normalfont\normalsize\itshape}}% style
\makeatother

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Commands / Notation
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\mpp}{\textsc{MRPP}\xspace}
\newcommand{\ilp}{\textsc{ILP}\xspace}
\newcommand{\cbs}{\textsc{CBS}\xspace}
\newcommand{\ecbs}{\textsc{ECBS}\xspace}
\newcommand{\decbs}{\textsc{DCBS}\xspace}
\newcommand{\secbs}{\textsc{SCBS}\xspace}
\newcommand{\ddm}{\textsc{DDM}\xspace}
\newcommand{\mapf}{\textsc{MAPF}\xspace}
\newcommand{\mcp}{\textsc{MCP}\xspace}
\newcommand{\makespan}{\textsc{MKPN}\xspace}
\newcommand{\soc}{\textsc{SOC}\xspace}
\newcommand{\noc}{\textsc{NOC}\xspace}
\newcommand{\dcr}{\textsc{DCR}\xspace}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Title
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\font\titlefont=ptmb at 14.7pt
%title{\titlefont Algorithm Designs of Parking and Retrieval of a Grid Based Shuttle Autonomous Parking System
%}
%\title{High Density Multi-Car Parking and Retrieving in an Autonomous Grid Based System
%}
\title{
%Optimizing Multi-Robot Path Planning in Crowded Environments with Efficient Heuristics
Efficient Heuristics for Multi-Robot Path Planning in Crowded Environments
}
\author{Teng Guo   \qquad Jingjin Yu% <-this % stops a space
\thanks{G. Teng, and J. Yu are with the Department of 
Computer Science, Rutgers, the State University of New Jersey, Piscataway, NJ, USA. 
Emails: {\tt\small \{ teng.guo, jingjin.yu\}@rutgers.edu}.
%This work is supported by NSF awards.
}
\thanks{This work was supported in part by NSF award IIS-1845888 and an Amazon Research Award.
}
}




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Title
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

\maketitle
\thispagestyle{empty}
\pagestyle{empty}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Latex editing related instructions for draft mode
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\ifdraft
\begin{picture}(0,0)%
\put(-12,105){
\framebox(505,40){\parbox{\dimexpr2\linewidth+\fboxsep-\fboxrule}{
\textcolor{blue}{
The file is formatted to look identical to the final compiled IEEE 
conference PDF, with additional margins added for making margin 
notes. Use $\backslash$todo$\{$...$\}$ for general side comments
and $\backslash$jy$\{$...$\}$ for JJ's comments. Set 
$\backslash$drafttrue to $\backslash$draftfalse to remove the 
formatting. 
}}}}
\end{picture}
\vspace*{-5mm}
\fi

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Main text
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
Optimal Multi-Robot Path Planning (\mpp) has garnered significant attention due to its many applications in domains including warehouse automation, transportation, and swarm robotics. 
% 
Current \mpp solvers can be divided into reduction-based, search-based, and rule-based categories, each with their strengths and limitations. 
% 
Regardless of the methodology, however, the issue of handling dense \mpp instances remains a significant challenge, where existing approaches generally demonstrate a dichotomy regarding solution optimality and efficiency.  
% 
This study seeks to bridge the gap in optimal \mpp resolution for dense, highly-entangled scenarios, with potential applications to high-density storage systems and traffic congestion control. 
%
Toward that goal, we analyze the behaviors of SOTA \mpp algorithms in dense settings and develop two hybrid algorithms leveraging the strengths of existing SOTA algorithms: \decbs (database-accelerated enhanced conflict-based search) and \secbs (sparsified enhanced conflict-based search). 
% 
Experimental validations demonstrate that \decbs and \secbs deliver a significant reduction in computational time compared to existing bounded-suboptimal methods and improve solution quality compared to existing rule-based methods, achieving a desirable balance between computational efficiency and solution optimality.
%
As a result, \decbs and \secbs are particularly suitable for quickly computing good-quality solutions for multi-robot routing in dense settings. 

\vspace{2mm}
\noindent Simulation video: \url{https://youtu.be/dZxMPUr7Bqg}\\
\noindent Upon the publication of the manuscript, source code and data will be released at \url{https://github.com/arc-l/dcbs}
\end{abstract}

\section{Introduction}\label{sec:intro}
\input{texs/00-intro}
%\section{Related Works}\label{sec:related}
\input{texs/01-related}

\section{Preliminaries}\label{sec:problem}
\input{texs/02-prelim}



\section{Database Conflict Resolution in \ecbs}\label{sec:algo-ddecbs}
\input{texs/05-algo-ddecbs.tex}
\section{Configuration Sparsification}\label{sec:algo-trans}
\input{texs/03-algo-trans.tex}






\section{Evaluation}\label{sec:evaluation}
\input{texs/06-evaluation}

\vspace{-1mm}
\section{Conclusion and Discussions}\label{sec:conclusion}
\input{texs/07-conclusion.tex}

% \newpage
%{\small
\bibliographystyle{formatting/IEEEtran}
\begin{thebibliography}{10}
\providecommand{\url}[1]{#1}
\csname url@rmstyle\endcsname
\providecommand{\newblock}{\relax}
\providecommand{\bibinfo}[2]{#2}
\providecommand\BIBentrySTDinterwordspacing{\spaceskip=0pt\relax}
\providecommand\BIBentryALTinterwordstretchfactor{4}
\providecommand\BIBentryALTinterwordspacing{\spaceskip=\fontdimen2\font plus
\BIBentryALTinterwordstretchfactor\fontdimen3\font minus
  \fontdimen4\font\relax}
\providecommand\BIBforeignlanguage[2]{{%
\expandafter\ifx\csname l@#1\endcsname\relax
\typeout{** WARNING: IEEEtran.bst: No hyphenation pattern has been}%
\typeout{** loaded for the language `#1'. Using the pattern for}%
\typeout{** the default language instead.}%
\else
\language=\csname l@#1\endcsname
\fi
#2}}

\bibitem{YuLav13AAAI}
J.~Yu and S.~M. LaValle, ``Structure and intractability of optimal multi-robot
  path planning on graphs,'' in \emph{Proceedings AAAI National Conference on
  Artificial Intelligence}, 2013, pp. 1444--1449.

\bibitem{Sur10}
P.~Surynek, ``An optimization variant of multi-robot path planning is
  intractable,'' in \emph{Proceedings AAAI National Conference on Artificial
  Intelligence}, 2010, pp. 1261--1263.

\bibitem{Yu2015IntractabilityPlanar}
J.~Yu, ``Intractability of optimal multi-robot path planning on planar
  graphs,'' \emph{IEEE Robotics and Automation Letters}, vol.~1, no.~1, pp.
  33--40, 2016.

\bibitem{wurman2008coordinating}
P.~R. Wurman, R.~D'Andrea, and M.~Mountz, ``Coordinating hundreds of
  cooperative, autonomous vehicles in warehouses,'' \emph{AI magazine},
  vol.~29, no.~1, pp. 9--9, 2008.

\bibitem{mason2019developing}
R.~Mason, ``Developing a profitable online grocery logistics business:
  Exploring innovations in ordering, fulfilment, and distribution at ocado,''
  in \emph{Contemporary Operations and Logistics}.\hskip 1em plus 0.5em minus
  0.4em\relax Springer, 2019, pp. 365--383.

\bibitem{wan2018lifelong}
Q.~Wan, C.~Gu, S.~Sun, M.~Chen, H.~Huang, and X.~Jia, ``Lifelong multi-agent
  path finding in a dynamic environment,'' in \emph{2018 15th International
  Conference on Control, Automation, Robotics and Vision (ICARCV)}.\hskip 1em
  plus 0.5em minus 0.4em\relax IEEE, 2018, pp. 875--882.

\bibitem{PodSuk04}
S.~Poduri and G.~S. Sukhatme, ``Constrained coverage for mobile sensor
  networks,'' in \emph{Proceedings IEEE International Conference on Robotics \&
  Automation}, 2004.

\bibitem{cheein2013agricultural}
F.~A.~A. Cheein and R.~Carelli, ``Agricultural robotics: Unmanned robotic
  service units in agricultural tasks,'' \emph{IEEE industrial electronics
  magazine}, vol.~7, no.~3, pp. 48--58, 2013.

\bibitem{RusDonJen95}
D.~Rus, B.~Donald, and J.~Jennings, ``Moving furniture with teams of autonomous
  robots,'' in \emph{Proceedings IEEE/RSJ International Conference on
  Intelligent Robots \& Systems}, 1995, pp. 235--242.

\bibitem{preiss2017crazyswarm}
J.~A. Preiss, W.~H{\"o}nig, G.~S. Sukhatme, and N.~Ayanian, ``Crazyswarm: A
  large nano-quadcopter swarm,'' in \emph{IEEE Int. Conf. on Robotics and
  Automation (ICRA)}, 2017.

\bibitem{KorMilSpi84}
D.~Kornhauser, G.~Miller, and P.~Spirakis, ``Coordinating pebble motion on
  graphs, the diameter of permutation groups, and applications,'' in
  \emph{Proceedings IEEE Symposium on Foundations of Computer Science}, 1984,
  pp. 241--250.

\bibitem{ErdLoz86}
M.~A. Erdmann and T.~Lozano-P\'erez, ``On multiple moving objects,'' in
  \emph{Proceedings IEEE International Conference on Robotics \& Automation},
  1986, pp. 1419--1424.

\bibitem{LavHut98b}
S.~M. LaValle and S.~A. Hutchinson, ``Optimal motion planning for multiple
  robots having independent goals,'' \emph{IEEE Transactions on Robotics \&
  Automation}, vol.~14, no.~6, pp. 912--925, Dec. 1998.

\bibitem{GuoPar02}
Y.~Guo and L.~E. Parker, ``A distributed and optimal motion planning approach
  for multiple mobile robots,'' in \emph{Proceedings IEEE International
  Conference on Robotics \& Automation}, 2002, pp. 2612--2619.

\bibitem{YuLav16TRO}
J.~Yu and S.~M. LaValle, ``Optimal multi-robot path planning on graphs:
  Complete algorithms and effective heuristics,'' \emph{IEEE Transactions on
  Robotics}, vol.~32, no.~5, pp. 1163--1177, 2016.

\bibitem{boyarski2015icbs}
E.~Boyarski, A.~Felner, R.~Stern, G.~Sharon, O.~Betzalel, D.~Tolpin, and
  E.~Shimony, ``Icbs: The improved conflict-based search algorithm for
  multi-agent pathfinding,'' in \emph{Eighth Annual Symposium on Combinatorial
  Search}, 2015.

\bibitem{cohen2016improved}
L.~Cohen, T.~Uras, T.~Kumar, H.~Xu, N.~Ayanian, and S.~Koenig, ``Improved
  bounded-suboptimal multi-agent path finding solvers,'' in \emph{International
  Joint Conference on Artificial Intelligence}, 2016.

\bibitem{Guo2023TowardEP}
T.~Guo and J.~Yu, ``Toward efficient physical and algorithmic design of
  automated garages,'' \emph{arXiv preprint arXiv:2302.01305}, 2023.

\bibitem{okoso2022high}
A.~Okoso, K.~Otaki, S.~Koide, and T.~Nishi, ``High density automated valet
  parking via multi-agent path finding,'' in \emph{2022 IEEE 25th International
  Conference on Intelligent Transportation Systems (ITSC)}.\hskip 1em plus
  0.5em minus 0.4em\relax IEEE, 2022, pp. 2146--2153.

\bibitem{han2019ddm}
S.~D. Han and J.~Yu, ``Ddm: Fast near-optimal multi-robot path planning using
  diversified-path and optimal sub-problem solution database heuristics,''
  \emph{ArXiv}, vol. abs/1904.02598, 2019.

\bibitem{sharon2015conflict}
G.~Sharon, R.~Stern, A.~Felner, and N.~R. Sturtevant, ``Conflict-based search
  for optimal multi-agent pathfinding,'' \emph{Artificial Intelligence}, vol.
  219, pp. 40--66, 2015.

\bibitem{guo2022sub}
T.~Guo and J.~Yu, ``{Sub-1.5 Time-Optimal Multi-Robot Path Planning on Grids in
  Polynomial Time},'' in \emph{Proceedings of Robotics: Science and Systems},
  New York City, NY, USA, June 2022.

\bibitem{stern2019multi}
R.~Stern, N.~Sturtevant, A.~Felner, S.~Koenig, H.~Ma, T.~Walker, J.~Li,
  D.~Atzmon, L.~Cohen, T.~Kumar, \emph{et~al.}, ``Multi-agent pathfinding:
  Definitions, variants, and benchmarks,'' \emph{arXiv preprint
  arXiv:1906.08291}, 2019.

\bibitem{surynek2010optimization}
P.~Surynek, ``An optimization variant of multi-robot path planning is
  intractable,'' in \emph{Proceedings of the AAAI Conference on Artificial
  Intelligence}, vol.~24, no.~1, 2010.

\bibitem{yu2013structure}
J.~Yu and S.~M. LaValle, ``Structure and intractability of optimal multi-robot
  path planning on graphs,'' in \emph{Twenty-Seventh AAAI Conference on
  Artificial Intelligence}, 2013.

\bibitem{ma2016multi}
H.~Ma, C.~Tovey, G.~Sharon, T.~Kumar, and S.~Koenig, ``Multi-agent path finding
  with payload transfers and the package-exchange robot-routing problem,'' in
  \emph{Proceedings of the AAAI Conference on Artificial Intelligence},
  vol.~30, no.~1, 2016.

\bibitem{yu2016optimal}
J.~Yu and S.~M. LaValle, ``Optimal multirobot path planning on graphs: Complete
  algorithms and effective heuristics,'' \emph{IEEE Transactions on Robotics},
  vol.~32, no.~5, pp. 1163--1177, 2016.

\bibitem{erdem2013general}
E.~Erdem, D.~G. Kisa, U.~{\"O}ztok, and P.~Schueller, ``A general formal
  framework for pathfinding problems with multiple agents.'' in \emph{AAAI},
  2013.

\bibitem{guo2021spatial}
T.~Guo, S.~D. Han, and J.~Yu, ``Spatial and temporal splitting heuristics for
  multi-robot motion planning,'' in \emph{2021 IEEE International Conference on
  Robotics and Automation (ICRA)}, 2021, pp. 8009--8015.

\bibitem{hart1968formal}
P.~E. Hart, N.~J. Nilsson, and B.~Raphael, ``A formal basis for the heuristic
  determination of minimum cost paths,'' \emph{IEEE transactions on Systems
  Science and Cybernetics}, vol.~4, no.~2, pp. 100--107, 1968.

\bibitem{silver2005cooperative}
D.~Silver, ``Cooperative pathfinding.'' \emph{AIIDE}, vol.~1, pp. 117--122,
  2005.

\bibitem{sharon2013increasing}
G.~Sharon, R.~Stern, M.~Goldenberg, and A.~Felner, ``The increasing cost tree
  search for optimal multi-agent pathfinding,'' \emph{Artificial Intelligence},
  vol. 195, pp. 470--495, 2013.

\bibitem{barer2014suboptimal}
M.~Barer, G.~Sharon, R.~Stern, and A.~Felner, ``Suboptimal variants of the
  conflict-based search algorithm for the multi-agent pathfinding problem,'' in
  \emph{Seventh Annual Symposium on Combinatorial Search}, 2014.

\bibitem{okumura2019priority}
K.~Okumura, M.~Machida, X.~D{\'e}fago, and Y.~Tamura, ``Priority inheritance
  with backtracking for iterative multi-agent path finding,'' \emph{arXiv
  preprint arXiv:1901.11282}, 2019.

\bibitem{luna2011push}
R.~J. Luna and K.~E. Bekris, ``Push and swap: Fast cooperative path-finding
  with completeness guarantees,'' in \emph{Twenty-Second International Joint
  Conference on Artificial Intelligence}, 2011.

\bibitem{szegedy2020rearrangement}
M.~Szegedy and J.~Yu, ``On rearrangement of items stored in stacks,'' in
  \emph{The 14th International Workshop on the Algorithmic Foundations of
  Robotics}, 2020.

\bibitem{GuoFenYu22IROS}
T.~Guo, S.~W. Feng, and J.~Yu, ``{Polynomial Time Near-Time-Optimal Multi-Robot
  Path Planning in Three Dimensions with Applications to Large-Scale UAV
  Coordination},'' in \emph{2022 IEEE/RSJ International Conference on
  Intelligent Robots and Systems (IROS)}, 2022.

\bibitem{pearl1982studies}
J.~Pearl and J.~H. Kim, ``Studies in semi-admissible heuristics,'' \emph{IEEE
  transactions on pattern analysis and machine intelligence}, no.~4, pp.
  392--399, 1982.

\bibitem{yu2012distance}
J.~Yu and M.~LaValle, ``Distance optimal formation control on graphs with a
  tight convergence time guarantee,'' in \emph{2012 IEEE 51st IEEE Conference
  on Decision and Control (CDC)}.\hskip 1em plus 0.5em minus 0.4em\relax IEEE,
  2012, pp. 4023--4028.

\bibitem{yu2013multi}
J.~Yu and S.~M. LaValle, ``Multi-agent path planning and network flow,'' in
  \emph{Algorithmic foundations of robotics X}.\hskip 1em plus 0.5em minus
  0.4em\relax Springer, 2013, pp. 157--173.

\bibitem{ma2016information}
K.-C. Ma, L.~Liu, and G.~S. Sukhatme, ``An information-driven and
  disturbance-aware planning method for long-term ocean monitoring,'' in
  \emph{Intelligent Robots and Systems (IROS), 2016 IEEE/RSJ International
  Conference on}.\hskip 1em plus 0.5em minus 0.4em\relax IEEE, 2016, pp.
  2102--2108.

\bibitem{stern2019mapf}
R.~Stern, N.~R. Sturtevant, A.~Felner, S.~Koenig, H.~Ma, T.~T. Walker, J.~Li,
  D.~Atzmon, L.~Cohen, T.~K.~S. Kumar, E.~Boyarski, and R.~Bartak,
  ``Multi-agent pathfinding: Definitions, variants, and benchmarks,''
  \emph{Symposium on Combinatorial Search (SoCS)}, pp. 151--158, 2019.

\end{thebibliography}

%}



\end{document}