\section{Conclusion}
In this work, we propose IMAGINE, a novel and general framework designed to not only integrate the sophisticated reasoning and planning capabilities of Multi-Agent System into a single, compact language model but also to significantly surpass the capabilities of the original Multi-Agent System. Our method significantly enhances the performance of a single language model on complex reasoning and planning tasks, while completely avoiding the inherent limitations of Multi-Agent Systems (such as high inference costs and significant latency due to multi-turn interactions, and difficulties in end-to-end training).

Extensive experiments on the highly challenging TravelPlanner benchmark demonstrate the effectiveness of our approach. After training with our method, our 8B model achieves an 82.7\% Final Pass Rate on the TravelPlanner test set (1000 queries), significantly outperforming models such as GPT-4o (7\%) and DeepSeek-R1-671B (40\%), and surpassing our carefully designed Multi-Agent System (45.8\%) by a notable margin. Furthermore, the model exhibits substantial improvements across all evaluation criteria.

In addition to its exceptional performance, IMAGINE offers substantial practical advantages. The resulting single model operates with high efficiency, eliminating the need for multi-turn internal interactions or complex procedural workflows. This leads to a significant reduction in inference latency, inference cost, and deployment overhead. Its compact model size, combined with end-to-end trainability, ensures high scalability and ease of deployment. This study establishes a new paradigm for developing powerful and efficient reasoning models, demonstrating that a single model trained with our method can indeed learn and ultimately surpass the capabilities of a well-organized multi-agent team.
