\documentclass[11pt, letterpaper]{article}

\usepackage{games}
\usepackage{verbatim}
%\input{content/glossary}

% changing the following can be used to toggle author notes between on and off

\usepackage{tikz}
\thispagestyle{empty}

\begin{document}

\title{Approximating Nash Equilibrium in Random Graphical Games}
\author{ Morris Yau \thanks{ \texttt{morrisy@mit.edu}}}
\affil{Massachusetts Institute of Technology}
\date{\today}
\maketitle

\begin{abstract}
       Computing Nash equilibrium in multi-agent games is a longstanding challenge at the interface of game theory and computer science.  It is well known that a general normal form game in $N$ players and $k$ strategies requires exponential space simply to write down.  This \emph{Curse of Multi-Agents} prompts the study of \emph{succinct} games which can be written down efficiently.  A canonical example of a \emph{succinct} game is the \emph{graphical game} which models players as nodes in a graph interacting with only their neighbors in direct analogy with markov random fields.  Graphical games have found applications in wireless, financial, and social networks.  However, computing the nash equilbrium of graphical games has proven challenging. Even for \emph{polymatrix} games, a model where payoffs to an agent can be written as the sum of payoffs of interactions with the agent's neighbors, it has been shown that computing an $\epsilon$ approximate nash equilibrium is PPAD hard for $\epsilon$ smaller than a constant.  The focus of this work is to circumvent this computational hardness by considering average case graph models i.e random graphs.  We provide a quasipolynomial time approximation scheme (QPTAS) for computing an $\epsilon$ approximate nash equilibrium of polymatrix games on random graphs with edge density greater than $\poly(k, \frac{1}{\epsilon}, \ln(N))$ with high probability.  Furthermore, with the same runtime we can compute an $\epsilon$-approximate Nash equilibrium that $\epsilon$-approximates the maximum social welfare of any nash equilibrium of the game.  Our primary technical innovation is an "accelerated rounding" of a novel hierarchical convex program for the nash equilibrium problem.  Our accelerated rounding also yields faster algorithms for Max-2CSP on the same family of random graphs, which may be of independent interest.  
       
\end{abstract}



\thispagestyle{empty}
\setcounter{page}{0}
\newpage

\tableofcontents

\thispagestyle{empty}
\setcounter{page}{0}
\newpage

\input{algorithm}
%\input{/introduction}
%\input{content/techniques-final}
%\input{content/prelim}
%\input{content/algorithms}
%\input{content/proof_of_algorithms}
%\input{content/solver_analysis}
%\input{content/powermethod}
%\input{content/fastprojection}
%\input{content/graphs}

\section*{Acknowledgements}
The author would like to thank Prasad Raghavendra, Ankur Moitra, and Costis Daskalakis for helpful discussions.
\newpage
\bibliographystyle{alpha}
\bibliography{bibliography}

\appendix

\input{appendix}

\end{document}