\section{On Presentations of Pure Braid Groups}\label{appendix:pn}
\citet{bhattacharya2018path} gave a presentation of a homotopy group for path planning with $n$ agents on a plane, which is a pure braid group $P_n$, with the following generators:
\begin{equation}
\left\{u_{i,j/\gamma_{i+1},\ldots,\gamma_{j-1}}\middle|1\leq i<j\leq n,\,\gamma_{i+1},\ldots,\gamma_{j-1}\in\{+,-\}\right\}.
\end{equation}

The relations are as follows.
\begin{itemize}
    \item For $i<j<k$, $\alpha_{i+1},\ldots,\alpha_{j-1}\in\{+,-\}$, and $\beta_{j+1},\ldots,\beta_{k-1}\in\{+,-\}$,
    \begin{equation}
    \begin{split}
    &u_{i,j/\alpha_{i+1},\ldots,\alpha_{j-1}}
    \cdot
        u_{i,k/\alpha_{i+1},\ldots,\alpha_{j-1},-,\beta_{j+1},\ldots,\beta_{k-1}}
        \cdot u_{j,k/\beta_{j+1},\ldots,\beta_{k-1}}\\
        &\cdot u^{-1}_{i,j/\alpha_{i+1},\ldots,\alpha_{j-1}}
    \cdot
        u^{-1}_{i,k/\alpha_{i+1},\ldots,\alpha_{j-1},+,\beta_{j+1},\ldots,\beta_{k-1}} 
        \cdot u^{-1}_{j,k/\beta_{j+1},\ldots,\beta_{k-1}},
    \end{split}
    \end{equation}
    \begin{equation}
    \begin{split}
    &u_{i,j/\alpha_{i+1},\ldots,\alpha_{j-1}}
    \cdot
        u_{i,k/\alpha_{i+1},\ldots,\alpha_{j-1},-,\beta_{j+1},\ldots,\beta_{k-1}}\\
        &\cdot u^{-1}_{i,j/\alpha_{i+1},\ldots,\alpha_{j-1}}\cdot
        u^{-1}_{i,k/\alpha_{i+1},\ldots,\alpha_{j-1},+,\beta_{j+1},\ldots,\beta_{k-1}},
    \end{split}
    \end{equation}
    and
    \begin{equation}\label{eq:p-rel}
    \begin{split}
    &u_{i,k/\alpha_{i+1},\ldots,\alpha_{j-1},-,\beta_{j+1},\ldots,\beta_{k-1}}
        \cdot u_{j,k/\beta_{j+1},\ldots,\beta_{k-1}}\\
    &\cdot u^{-1}_{i,k/\alpha_{i+1},\ldots,\alpha_{j-1},+,\beta_{j+1},\ldots,\beta_{k-1}} 
    \cdot u^{-1}_{j,k/\beta_{j+1},\ldots,\beta_{k-1}}.
    \end{split}
    \end{equation}
\item Let $i,j,i',j'$ be distinct indices with $i<j,\,i'<j',\,i<i'$. Let $\gamma_{i+1},\ldots,\gamma_{j-1}\in\{+,-\}$ and $\gamma'_{i'+1},\ldots,\gamma'_{j'-1}\in\{+,-\}$ be signs.
When $i<i'<j<j'$, we assume that $\gamma_{i'}\neq \gamma'_j$ and $(\gamma_k,\gamma'_k)\neq(-\gamma_{i'},\gamma_{i'})$ for all $i'<k<j$.
When $i<i'<j'<j$, we assume that $\gamma_{i'}= \gamma_{j'}$ and $(\gamma_k,\gamma'_k)\neq(-\gamma_{i'},\gamma_{i'})$ for all $i'<k<j'$. For such tuples,
    \begin{equation}\label{eq:commute}
    \begin{split}
    &u_{i,j/\gamma_{i+1},\ldots,\gamma_{j-1}}
    \cdot u_{i',j'/\gamma'_{i'+1},\ldots,\gamma'_{j'-1}}
    \cdot u^{-1}_{i,j/\gamma_{i+1},\ldots,\gamma_{j-1}}
    \cdot u^{-1}_{i',j'/\gamma'_{i'+1},\ldots,\gamma'_{j'-1}}.
    \end{split}
    \end{equation}
\end{itemize}
The description in the original paper is incomplete as it omits the condition for the relation (\ref{eq:commute}).

We consider the word
\begin{equation}
w=u_{1,4/--}u_{2,4/-}u_{3,4}u_{1,4/++}^{-1}u_{2,4/+}^{-1}u_{3,4}^{-1},
\end{equation}
which is irreducible when using Dehn's algorithm.
On the other hand,
\begin{equation}
\begin{split}
w &=u_{2,4/-}u_{1,4/+-}u_{3,4}u_{1,4/++}^{-1}u_{2,4/+}^{-1}u_{3,4}^{-1}\\
&=u_{2,4/-}u_{3,4}u_{2,4/+}^{-1}u_{3,4}^{-1}\\
&=u_{3,4}u_{3,4}^{-1}\\
&=e,
\end{split}
\end{equation}
where the first, second, and third equalities are deduced from (\ref{eq:p-rel}) with $(i,j,k)=(1,2,4)$, $(1,3,4)$, and $(2,3,4)$, respectively. Thus, Dehn's algorithm is incomplete for this presentation when $n\geq 4$.

The pure braid group $P_n$ has a standard presentation~\citep{rolfsen2010tutorial} using generators $\left\{a_{i,j}\middle|1\leq i<j\leq n\right\}$ with notation (\ref{eq:def_a})
and the following relations.
\begin{itemize}
\item For $1\leq i<j<k\leq n$,
\begin{equation}
    a_{i,j}a_{i,k}a_{j,k}a_{i,j}^{-1}a_{j,k}^{-1}a_{i,k}^{-1},
\end{equation}
and
\begin{equation}
    a_{i,k}a_{j,k}a_{i,j}a_{i,k}^{-1}a_{i,j}^{-1}a_{j,k}^{-1}.
\end{equation}
\item For $1\leq i<j<k<l\leq n$,
\begin{equation}
    a_{i,j}a_{k,l}a_{i,j}^{-1}a_{k,l}^{-1},
\end{equation}
\begin{equation}
    a_{i,l}a_{j,k}a_{i,l}^{-1}a_{j,k}^{-1},
\end{equation}
and
\begin{equation}
    a_{i,k}a_{j,k}a_{j,l}a_{j,k}^{-1}a_{i,k}^{-1}a_{j,k}a_{j,l}^{-1}a_{j,k}^{-1}.
\end{equation}
\end{itemize}
Let
\begin{equation}
u_{i,j/\sigma_{i+1},\ldots,\sigma_{j-1}}=a_{i,i+1}^{d_{i+1}}\cdots a_{i,j-1}^{d_{j-1}} a_{i,j}a_{i,j-1}^{-d_{j-1}}\cdots a_{i,i+1}^{-d_{i+1}},
\end{equation}
where $d_k=1$ if $\sigma_k=+$, and $d_k=0$ if $\sigma_k=-$.
Then, the relations for $\{u_{i,j/\sigma_{i+1},\ldots,\sigma_{j-1}}\}$ can be deduced from the relations for $\{a_{i,j}\}$ and vice versa. Therefore, we can translate words from Bhattacharya and Ghrist's presentation to words for the standard presentation. However, this translation increases the lengths of words by a factor of $O(n)$.
On the other hand, lengths of words constructed by Bhattacharya and Ghrist's method are equal to those of words constructed by the method in \S~\ref{subsec:word construction}.
To the best of our knowledge, there is no algorithm for the word problem of the pure braid group that is efficient enough to compensate for these drawbacks. This is why we use elements of the braid group to label homotopy classes, instead of those of the pure braid group.

\section{Proof of Proposition~\ref{prop:homotopy_inj}}\label{appendix:proof}
The map from $\mathcal{C}_{r+n}(\mathbb{R}^2)$ to $\mathcal{C}_r(\mathbb{R}^2)$, which sends $(p_1,\ldots,p_{r+n})$ to $(p_1,\ldots,p_r)$, is a fiber bundle~\citep{fadell1962configuration}, and the fiber at $(o_1,\ldots, o_r)$ is the image of the embedding (\ref{eq:embedding}). Thus, the following exact sequence of homotopy groups is induced:
\begin{equation}        
\pi_2\left(\mathcal{C}_r(\mathbb{R}^2)\right)\to
\pi_1\left(\mathcal{C}_n(\mathbb{R}^2\setminus\{o_1,\ldots,o_r\})\right)\to \pi_1\left(\mathcal{C}_{r+n}(\mathbb{R}^2)\right),
\end{equation}
where $\pi_2\left(\mathcal{C}_r(\mathbb{R}^2)\right)$ is the second homotopy group of $\mathcal{C}_r(\mathbb{R}^2)$~\citep{hatcher2002algebraic}.
Moreover, $\pi_2\left(\mathcal{C}_r(\mathbb{R}^2)\right)$ is trivial~\citep{knudsen2018configuration}.
