A number of use cases of planning rose in information-gathering missions from
the development of unmanned autonomous vehicles (UAVs). For instance, in search
and rescue missions, a fleet of drones can cover a lot of ground in a short
amount of time and report any finding to a mission supervisor to narrow the
search for the rescue team. Other examples are the analysis of terrain for smart
farms and in hazardous locations. For this kind of missions, the information
gathered is used for decision making at a supervising station. Thus, the drones
need to be constantly in communication with the station to report the gathered information
during the mission. The use of multiple UAVs to cover an area not only reduces the time
required to complete the mission but can also enable reaching locations which would
not be reachable with a single drone due to connection constraints.
%be used to reach some location,
%where a single one cannot, without losing the connection with the supervisor.
\iffull
\else
\blfootnote{$^1$\href{https://drive.google.com/open?id=1dmvAWjN6vNwxGIBw9TmXCOjw3gKCZWoh}{https://drive.google.com/open?id=1dmvAWjN6vNwxGIBw9T\newline mXCOjw3gKCZWoh}}
\fi
The original multi-agent path planning problem asks for a plan to reach a
configuration of agents in a graph. However, an important problem for search and
rescue missions or terrain analysis is the coverage of an area. We thus study
both the coverage problem and the reachability problem under a connection
constraint over the agents which requires them to be connected to the base
either directly or via another agent, who can relay its data. We establish the
computational complexity of the connected coverage in its general case and for a
practical subclass introduced recently~\cite{dblp:conf/aaai/tateobrab18} in
which the UAVs can communicate with others located within one step, called the
\emph{neighbor-communicable} topological graphs. We show that the coverage is
PSPACE-complete in the general case, and remains so for neighbor-communicable
topological graphs. Thus, restricting to neighbor-communicable graphs does not
render the problem feasible, and the relatively high complexity unfortunately
remains. Note that this is in line with the PSPACE-completeness of the
reachability problem recently reported in~\cite{dblp:conf/aaai/tateobrab18}.
%Note that the PSPACE-completeness of the reachability problem was recently shown~


% We show that, in the
% general case, the complexity of deciding whether the coverage is achievable is
% PSPACE-complete and that this complexity result holds on the
% neighbor-communicable topological graphs.
%\textbf{\textcolor{red}{TODO: CITE RETINA}}

Our main result in this paper is the definition of a class of topological graphs
which is well adapted and realistic for UAV missions, and for which the coverage
and reachability problems admit efficient solutions. Our subclass, called
\emph{sight-moveable} graphs, is defined assuming that the UAVs cannot
communicate through obstacles and are restricted to line-of-sight communication.
This class emerged from an ongoing case study for a drone assisted search and
rescue project in which the authors take part. For this class, we prove that
both the reachability and coverage problems are in LOGSPACE while the existence
of a bounded execution is in NP. This drastically changes the status of this
problem since by LOGSPACE $\subseteq$ NC (this is the class of problems solvable
in polylogarithmic time in a parallel machine with a polynomial number of
processors),
%\footnote{\todo[inline]{Explain NC !}}, 
%the LOGSPACE
%membership means that
one can build an efficient parallel algorithm~\cite{Cook:1979}.
The NP upper bound is also useful since this means efficient SAT solvers can be used directly
to compute bounded executions.
We prove that our algorithms for the bounded variants are optimal by showing NP-hardness
in each case.

%The motivation behind our subclass is the following.
%In some applications, the UAVs gather a large amount of data for a rigorous
%analysis. Hence, the connection between the UAVs and the supervising station
%needs to be reliable.
%the sight-moveable topological graphs.
%We show that deciding the existence of a
%feasible plan can be achieved by a logarithmic-space algorithm and that deciding
%of the existence of a bounded execution is NP-complete. 
%In addition to the
%reachability of a configuration, we study the problem of bounded and unbounded
%coverage on sight-moveable topological graphs. We claim that the unbounded
%version is in LOGSPACE, and the bounded version is NP-complete. 

\input{picture_execution}

In this work, we consider all agents to be anonymous in both cases (reachability
and coverage). Furthermore, we consider the collisions to be handled by the
agents themselves, hence are not considered along the results of this paper. We
depicted a covering execution of a topological graph by 3 UAVs in Figure
\ref{figure:exampleexecution}. In this example, the UAVs need to gather
information at each node of the graph while staying connected to the base (red
node) during the whole mission.

%The rest of the paper is structured as follows. 
In Section
\ref{sec:preli}, we present the typical notions used in MAPP and their extension
for our case and the known results in connected planning. In Sections
\ref{sec:dir} to \ref{sec:compl}, we study the complexity of our problems from the general case
to the most restrictive one. We describe the related works in Section \ref{sec:relate}.
%Finally, 
We conclude in Section \ref{sec:concl}.

\iffull
\else
\mbox{The full version of the paper\footnotemark[1] is available.}
\fi

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "main"
%%% End:
