The results in this subsection are based on a result of Reingold~\cite{Reingold:2008}, who
proved that the problem of checking the connectivity of two nodes $s$ and $t$ in an
undirected graph, namely \USTCONN, is in LOGSPACE.

\begin{theorem}
	\label{theorem:USTCONNinLOGSPACE}
	\USTCONN~ is in LOGSPACE \cite{Reingold:2008}.
\end{theorem}

\begin{proposition}\label{prop:sm:ub:reach}
	\pbReachSM is in LOGSPACE.
\end{proposition}

\begin{proof}
  The idea of the proof is to reduce \pbReachSM to \UCONN, that is the problem
  of deciding whether an undirected graph is connected. From
  Theorem~\ref{theorem:USTCONNinLOGSPACE}, we can reduce \UCONN~ to \USTCONN~
  by simply looping over all pairs of nodes ($\sourcenode, \targetnode)$ and
  checking for a path from $\sourcenode$ to $\targetnode$. Therefore, \UCONN~
  is in LOGSPACE.

  Now we describe the logarithmic space reduction of \pbReachSM
  \linebreak[4]
  to \UCONN. Let $G=\langle \setnodes, \moves, \coms \rangle$ a sight-moveable
    topological graph and $c$ a configuration. Let $\setnodes' = \set{c_1,
    \dots, c_n, \basenode}$. The configuration $c$ is reachable iff the
    restriction of $\myundirectedgraph := (\setnodes, \coms)$ to the nodes in
    $\setnodes'$ is $\coms$-connected. Indeed, if it is, then $c$ is reachable:
    each agent follows some $\moves$-path from $\basenode$ to $c_i$ contained in
    a $\coms$-path from $\basenode$ to $c_i$. In other words, $(G, c)$ is a
    positive \pbReachSM-instance iff $\myundirectedgraph$ is a positive
    \UCONN-instance. The reduction is in logarithmic space: we compute
    $\myundirectedgraph$ by enumerating all $(u, v)$ $\coms$-edges in $G$, and
    we output $(u, v)$ when $u, v \in \setnodes'$. We recall that we only take
    into account the working memory for computing $\myundirectedgraph$; the
    output -- $\myundirectedgraph$ itself -- is not taken into account in the
    used space (see e.g. \cite{DBLP:books/daglib/0086373}, Ch. 8, Def. 8.21).
\end{proof}



%We denote $Comm(S)=\{v \in V / \exists u \in S, v \coms u\}$ the set of nodes
%which communicates with a node in $S$.
%We obtain that the algorithm \pbReachSM is sound and complete for the problem
%of reachability of a configuration in a topological graph. The \pbReachSM
%problem is then in P given that the algorithm \pbReachSM computes the fixed
%point on $S$ in polynomial-time.

% \end{comment}


\begin{proposition}\label{prop:sm:ub:cover}
  \pbCoverageSM is in LOGSPACE.
\end{proposition}

\begin{proof}
  First we prove that the bounded version of the connectivity in undirected
  graphs is also in LOGSPACE.

  \begin{lemma}
    \label{lemma:boundedUSTCONNinLOGSPACE}
    Bounded-\USTCONN, that is the problem, giving an undirected graph
    $\myundirectedgraphbounded$, two nodes $\sourcenode, \targetnode$, an
    integer $n$ written in binary, of deciding whether there is a path of
    length at most $n$ from $\sourcenode$ to $\targetnode$ in $G$ is in
    LOGSPACE.
  \end{lemma}

  \begin{proof} We reduce Bounded-\USTCONN~ to \USTCONN~ in logarithmic space as
    follows. From a Bounded-\USTCONN~ instance $(\myundirectedgraphbounded,
    \sourcenode, \targetnode, n)$ we construct in logarithmic space a
    \USTCONN~ instance $(\myundirectedgraph, \sourcenode', \targetnode')$:
    \begin{inparaenum}
    \item The nodes of $\myundirectedgraph$ are pairs $(v, j)$ where $v$
      is a node of $\myundirectedgraphbounded$ and $j$ is an integer in
      $\set{0,n}$ but smaller than the number of nodes in
      $\myundirectedgraph$;
    \item $\myundirectedgraph$ contains an edge between $(v, j)$ and
      $(v', j+1)$ when there is an edge between $v$ and $v'$ in
      $\myundirectedgraphbounded$ or when $v = v'$;
    \item $\sourcenode' = (\sourcenode, 0)$ and $\targetnode' =
      (\targetnode', n)$.
    \end{inparaenum}
  \end{proof}

  Now let $G=\langle V, \moves, \coms \rangle$ be a sight-moveable topologic
  graph and $n$ an integer written in binary. To test whether $(G, n)$ is a
  positive instance of Coverage, it suffices to check that there is a path
  from any node $v$ to the base $B$ with at most $n$ communication edges. To
  do that, we test sequentially, for all $v$, that $((V, \coms), v, B, n)$ is
  a positive instance of Bounded-\USTCONN~. Thus, we obtain an algorithm in
  logarithmic space to decide Coverage.

\end{proof}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "main"
%%% End:
