%!TEX root = ./main.tex

\section{Further Experiments}
%\seclabel{app_experiments}
\applabel{app_experiments}

For the sake of completeness, here we report on a small experimental comparison with the SMT-based tool Dirk~\cite{Kalhauge2018}.
As the complexity of Dirk is polynomial (due to SMT solving), it uses windowing to examine segments of a large trace.
In our experiments we set a window size of 1.5K and timeout of $1$ hour.
Finally, our experiments were run on a subset of our dataset, as we faced technical challenges in executing Dirk on some benchmarks.
We nevertheless ensured that all tools were executed on identical inputs.
\cref{tab:expr-results-dirk} shows the obtained results.
We confirm that Dirk takes extremely long to complete even this subset and fails to report deadlocks on larger instances due to timeout, 
while it detects two deadlocks missed by our algorithms due to the fact that it also detects deadlocks not witnessed by correct reorderings.
In particular, Dirk reports a deadlock in the benchmarks Deadlock and Transfer.
The reordering that exposes these deadlocks changes the reads-from function so that reads observe different writes in the witness trace (which, nevertheless, write the same value as the old writes, and thus the witness is sound).
We remark that reasoning about reorderings based on values is a very intractable problem (well-known to be $\NP$-hard even for 3 threads), and thus methods based on such reasoning are not scalable.
Indeed, Dirk timed out after 1h on each benchmark that required at least 1 second in $\SyncPDOnline$ and $\SyncPDOffline$.
\input{tables/dirk_results}
