\section{New Cutoff Results}
\label{sec:cutoffs}

We present new cutoff results that extend Theorems~\ref{thm:disj-cutoff-pairs} and \ref{thm:conj-cutoff}, summarized in the table below. We distinguish between disjunctive and conjunctive systems, non-fair and fair executions, as well as between the satisfaction of $\LTLmX$ properties $h(A,B^{(k)})$ and the existence of deadlocks. All results hold for open systems, and for both path quantifiers $\pforall$ and $\pexists$. Cutoffs depend on the size of process template $B$ and the number $k \geq 1$ of $B$-processes a property talks about:
%
\begin{table}[h]
\centering
\vspace{-10pt}
\label{table:cutoffs}
\centering
\setlength{\tabcolsep}{2pt}
{%\resizebox{\linewidth}{!}{
\begin{tabular}{ r|c|c|c|c }
   & \specialcellC{$h(A,B^{(k)})$ \\ no fairness} & \specialcellC{deadlock detection \\ no fairness} & \specialcellC{$h(A,B^{(k)})$ \\ uncond. fairness} & \specialcellC{deadlock detection \\ strong fairness}  \\[9pt]
\hline
Disjunctive~ & $|B| + k + 1$ &
        $2|B| - 1$ & 
        $2|B| + k - 1$ &
        $2|B| - 1$ 
          \\[4pt]
\hline
Conjunctive~ & 
        $k+1$ &  
        $2|B|-2~(*)$ & 
        $k+1~(*)$ &  
        $2|B|-2~(*)$
\end{tabular}
}
\vspace{-10pt}
\end{table}

Results marked with a $(*)$ are for a restricted class of systems:
For conjunctive systems with fairness, we require infinite runs to be 
initializing, i.e., all non-deadlocked 
%$B$-processes 
processes 
return to 
$\init$
%$\initstate_B$ 
infinitely often.\footnote{This assumption is in the same 
flavor as the restriction that $\initstate_A$ and $\initstate_B$ appear in 
all conjunctive guards. Intuitively, the additional restriction makes sense 
since conjunctive systems model shared resources, and everybody who takes a 
resource should eventually release it.} Additionally, the cutoffs for 
deadlock detection in conjunctive systems only support 
$1$-conjunctive systems. The reason for this restriction will be
explained in Remark~\ref{rem:general-conj-tough}\iffinal.\else (and Appendix~\ref{sec:app-conj}).\fi

All cutoffs in the table are tight -- no smaller cutoff can exist for 
this class of systems and properties -- except for the case of deadlock 
detection in disjunctive systems without fairness. There, the cutoff is 
asymptotically tight, i.e., it must increase linearly with the size 
of the process template.

\input{proof-structure}
\input{proof-ideas-disj}
\input{proof-ideas-conj}
% \input{cutoffs-disj}
%\input{appendix-disj}
%\input{appendix-conj}
% \input{cutoffs-conj}
