\documentclass[a4paper,runningheads]{llncs}

\IfFileExists{cropped_pages}{
\paperwidth 13.2cm
\paperheight 21.3cm
\oddsidemargin  -0.85in
\evensidemargin -0.85in
\topmargin      -0.85in
}{}

%\usepackage{amsthm}
\input{preamble}

% hyperref goes last
\usepackage[colorlinks=true]{hyperref}
\hypersetup{%
  pdftitle={Tight Cutoffs for Guarded Protocols with Fairness},%
  pdfauthor={Simon Ausserlechner, Swen Jacobs, Ayrat Khalimov},%
  pdfsubject={},%
  pdfkeywords={\listOfKeywords},%
  colorlinks%
}

% Author macros::begin %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{Tight Cutoffs for\\ Guarded Protocols with Fairness}
\author{Simon Au{\ss}erlechner\inst{1}, Swen Jacobs\inst{2}, Ayrat Khalimov\inst{1}}
\institute{$^1$ IAIK, Graz University of Technology, Austria\\
					 $^2$ Reactive Systems Group, Saarland University, Germany}

\authorrunning{S. Au{\ss}erlechner, S. Jacobs and A. Khalimov}%mandatory. First: Use abbreviated first/middle names. Second (only in severe cases): Use first author plus 'et. al.'

%\keywords{\listOfKeywords}% mandatory: Please provide 1-5 keywords
\begin{document}
\iffinal
\else
  \textbf{TODOs:}
  \begin{itemize}
	\item \textbf{check conjunctive proofs}
	\item add (short) correctness arguments to proofs
	\item {\bf presentation of proof ideas in main part:}
	  \begin{itemize}
      \item pictures of main constructions?
	  \item explain why proofs do not work in general (for conj)
	  \end{itemize}
	\item \textbf{Notation}: 
	\begin{itemize}
	\item quantification over processes: unify $\forall i$ vs. $\forall p$, or explain difference
    \- we use 'conjunctive guarded system' and 'conjunctive system' -- unify SJ: we only have it in related work now, and cannot define 'conjunctive system' before
	\end{itemize}
	\item synthesize the running example
	\end{itemize}
	\textbf{Optional/Extensions:}
	\begin{itemize}
	\item tighten disjunctive deadlock detection
	\item conjunctive systems: extend to disjoint guards
	\item label-based cutoffs
	\item do we run into undecidability somewhere?\\ (label-based local deadlock detection?) (maybe: PMCP of push-down systems communicating via conj guards -- because for comm primitive $=$ unnested locks this is undec -- see Kahlon's CAV05 (reasoning about threads...) )
    \item disj: disj guards can be expressed in Petri nets. We can reduce to petri nets if we want to solve Global Deadlocks problem (anything else?)
    \item we consider the problem ``no global deadlocks $\land$ no local deadlocks under strong fairness $\land$ properties under undcond fairness''.
          An alternative is: ``no global deadlocks $\land$ properties under strong fairness''.
	\end{itemize}

\newpage

  \setcounter{tocdepth}{3}
  \tableofcontents
\fi

%
%
%
%\mainmatter              % start of the contributions
%

\maketitle              % typeset the title of the contribution
 \begin{abstract}
Guarded protocols were introduced in a seminal
paper by Emerson and Kahlon (2000), and describe systems of processes whose transitions
are enabled or disabled depending on the existence of other processes in
certain local states. We study parameterized model checking and synthesis of
guarded protocols, both aiming at formal correctness arguments for systems with any number of processes. 
Cutoff results reduce reasoning about systems with an arbitrary 
number of processes to systems of a determined, fixed size. Our work stems 
from the observation that existing cutoff results for guarded protocols i) are 
restricted to closed systems, and ii) are of limited use for liveness 
properties because reductions do not preserve fairness. We close these gaps
and obtain new cutoff results for open systems with liveness properties under
fairness assumptions. Furthermore, 
we obtain cutoffs for the detection of global and local deadlocks, which are of 
paramount importance in synthesis. Finally, we prove tightness or asymptotic tightness for the new cutoffs.
%, and show two examples automatically synthesized 
%by a prototype synthesizer.
\end{abstract} 

\input{intro}
\input{related}
\input{prelim}
\input{paramsynt}
\input{cutoffs}
\iffinal
\else
 \input{experiments}
\fi
\input{conclusion}
%\bibliographystyle{plain}
\bibliographystyle{splncs03}
\bibliography{paper,local,references,crossrefs}
%\iffinal
%\else
\appendix
\input{appendix}
%\fi

\end{document}
