

\section{Conclusion}

This paper present ReaSeq, a novel world-knowledge-reasoning paradigm that overcomes fundamental limitations of log-driven industrial ranking systems: knowledge poverty in ID-based representations causing brittle interest modeling under sparsity, and systemic blindness to beyond-log user interests. By integrating reasoning-enhanced representations that explicitly distill product attributes and user intents through multi-agent collaboration, and generative behavior reasoning that synthesizes latent beyond-log interactions via DLLMs, ReaSeq transforms recommendation from statistical pattern matching to knowledge-grounded generative reasoning. Full deployment on Taobao demonstrates significant gains (>6.0\% IPV, >6.0\% CTR, >2.9\% Orders, >2.5\% GMV), validating its breakthrough beyond the performance ceiling of conventional paradigms, which establishes a new foundation for recommendation systems to proactively model interests through world-aware reasoning rather than reactive log fitting. 

\textbf{Limitation and Future Work for GBR.} Although effective, our GBR still has some limitations that need to be addressed in future work: (i) The implemented \texttt{[FILL]} location schemes are naive heuristic strategies. As a starting point, we plan to introduce model-based strategies locate the beyond-log behavior more accurately in the future. (ii) The implemented GBR is a tiny, cold-start LLaDA, and thus its world knowledge is derived solely from the input reasoning-enhanced representations. In the future, we plan to use open-sourced LLaDA with its pre-trained weights to inject much more world knowledge into our GBR. (iii) In experiment our GBR was not applied to the reasoning-enhanced ranking paradigm (Section~\ref{sec:ranking}). Hence, we will explore adapting GBR to various ultra-long sequence modeling paradigms in the future.
