%$Id: md-via-sd.tex 266 2012-03-22 19:35:26Z saeed $

\documentclass[11pt]{article}

\usepackage{fullpage}

%\usepackage{bm}
\usepackage{dsfont}
\usepackage{latexsym}
\usepackage{natbib}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{aliascnt}
%\usepackage{fncylab}
%\usepackage[boxed,linesnumbered]{algorithm2e}
\usepackage{graphicx}
%\usepackage{color}
%\usepackage[margin=1in]{geometry}
\usepackage{enumerate}

%\usepackage[pdfpagelabels,pdfpagemode=None]{hyperref}
\usepackage{algorithmic}
\usepackage{algorithm}
\usepackage[pdfpagelabels,pdfpagemode=None]{hyperref}




\delimiterfactor=1100

\setlength{\delimitershortfall}{0pt}

\newcommand{\argmax}{\operatorname{arg\,max}}
\newcommand{\argmin}{\operatorname{arg\,min}}

\newtheorem{theorem}{Theorem}%
\newtheorem*{reltheorem}{Theorem}%

\newtheorem{lemma}{Lemma}%
\newcommand{\lemmaautorefname}{Lemma}

\newtheorem{claim}{Claim}%
\newcommand{\claimautorefname}{Claim}

\newtheorem{corollary}{Corollary}%
\newcommand{\corollaryautorefname}{Corollary}

\newtheorem{condition}{Condition}%
\newcommand{\conditionautorefname}{Cond.}

\newtheorem{proposition}{Proposition}%
\newcommand{\propositionautorefname}{Proposition}

\newtheorem{algo}{Algorithm}%
\newcommand{\algoautorefname}{Algorithm}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newcommand{\definitionautorefname}{Definition}

\newtheorem{example}{Example}
\newcommand{\exampleautorefname}{Ex.}

\newtheorem{remark}{Remark}
\newcommand{\remarkautorefname}{Remark}

\newcommand{\plan}[1]{

\noindent\fbox{\textbf{\color{red}PLAN: #1}} \index{PLAN}}

\newcommand{\todo}[1]{\noindent\fbox{\textbf{\color{red}TODO: #1}} \index{TODO}}

\DeclareMathOperator*{\E}{E}%
\DeclareMathOperator*{\cut}{Cut}%
\newcommand{\MyRETURN}{\STATE {\textbf{return }}}


\input{macros}
\input{notation}


\title{Bayesian Optimal Auctions \\ via Multi- to Single-agent Reduction}

\author{\hspace*{1in}
Saeed Alaei\thanks{email: \texttt{saeed@cs.umd.edu}, Dept.\ of Computer Science, University of Maryland, College Park, MD 20742.
Partially supported by ONR YIP grant N000141110662. Part of this work was done when the author was visiting Northwestern
University.  } \and Hu Fu\thanks{email: \texttt{hufu@cs.cornell.edu}. Dept.\ of Computer Science, Cornell University, Ithaca, NY
14853.  Supported by NSF grants CCF-0643934 and AF-0910940.  Part of this work was done when the author was visiting Northwestern
University.} \and Nima Haghpanah\thanks{email: \texttt{nima.haghpanah@gmail.com}. Dept.\ Electrical Engineering \& Computer
Science, Northwestern University, Evanston, IL 60201.} \hspace*{1in} \and Jason Hartline\thanks{email:
\texttt{hartline@eecs.northwestern.edu}. Dept.\ Electrical Engineering \& Computer Science, Northwestern University, Evanston, IL
60208.} \and Azarakhsh Malekian\thanks{email: \texttt{azarakhshm@gmail.com}. Dept.\ Electrical Engineering \& Computer Science,
Massachusetts Institute of Technology, Cambridge , MA 02139.} }

%\date{$ $Date: 2012-03-22 15:35:26 -0400 (Thu, 22 Mar 2012) $ $\protect\footnote{$ $Id: md-via-sd.tex 266 2012-03-22 19:35:26Z saeed $ $}}

\begin{document}
\maketitle


\input{abstract}
\input{intro}
\input{related}

\input{structure}

\input{prelim}

\input{single-agent}


\input{reduction}

\input{interims}

\input{border_1}

\input{border_k}

\input{border_matroid}

%\input{ptas}

\input{conc}

\bibliographystyle{apalike}
\bibliography{bibs}

\appendix
\input{border_1_appendix}
\input{border_k_appendix}
\input{border_matroid_appendix}

%\input{MRM'}
%\input{separation}
%\input{DPST}
%\input{regularity}

\end{document}
