% new_TLP2egui.tex / guide for TLP
% v2.12, released 23-apr-2003
%   (based on JFP2egui.tex v1.01) and tlp2egui.tex
% Copyright (C) 2000,2001,2002,2003, 2012 Cambridge University Press

\NeedsTeXFormat{LaTeX2e}

\documentclass{tlp}

\usepackage{mathptmx}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{setspace}
\usepackage{multirow}
%\usepackage{hyperref}
\usepackage{url}
\usepackage{stmaryrd}
\usepackage{verbatim}
\usepackage{ifthen}
\usepackage{pifont}
\usepackage{tipa}

\usepackage[mathscr]{eucal}

%%%%%%%%%% CODE FONT 
%\renewcommand*\ttdefault{txtt}
\renewcommand*\ttdefault{cmtt}
\newcommand{\myfontcodesize}{\fontsize{9}{9}}
\newcommand{\mytt}[1]{{\myfontcodesize \texttt{\textbf{#1}}}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newtheorem{theorem}{Theorem}
\newtheorem{proposition}{Proposition}


%%% Macros for the guide only %%%
\hyphenation{either}
\providecommand\AMSLaTeX{AMS\,\LaTeX}
\newcommand\eg{\emph{e.g.}\ }
\newcommand\etc{\emph{etc.}}
\newcommand\bcmdtab{\noindent\bgroup\tabcolsep=0pt%
  \begin{tabular}{@{}p{10pc}@{}p{20pc}@{}}}
\newcommand\ecmdtab{\end{tabular}\egroup}
\newcommand\rch[1]{$\longrightarrow\rlap{$#1$}$\hspace{1em}}
\newcommand\lra{\ensuremath{\quad\longrightarrow\quad}}

  \title[Applying CLP to SQL Semantic Analysis]%\tnoteref{thanks}]
  {Applying Constraint Logic Programming to\linebreak SQL Semantic Analysis\thanks{Work partially funded by the Spanish Ministry of Economy and Competitiveness, under the grant TIN2017-86217-R (CAVI-ART-2), and by the Madrid Regional Government, under the grant S2018/TCS-4339 (BLOQUES-CM), co-funded by EIE Funds of the European Union. Special thanks are due to the anonymous referees.
  	}
  }



  \author[F. S\'aenz-P\'erez]
         {FERNANDO S\'AENZ-P\'EREZ\\
         Complutense University of Madrid, 28040 Madrid, Spain\\
         \email{fernan@sip.ucm.es}}

%\jdate{March 2003}
%\pubyear{2003}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}
%\doi{S1471068401001193}

\newtheorem{lemma}{Lemma}[section]
\newtheorem{definition}{Definition}[section]
\newtheorem{example}{Example}[section]

\begin{document}

\label{firstpage}

\maketitle

\begin{abstract}
This paper proposes the use of Constraint Logic Programming (CLP) to model SQL queries in a data-independent abstract layer by focusing on some semantic properties for signalling possible errors in such queries.
First, we define a translation from SQL to Datalog, and from Datalog to CLP, so that solving this CLP program will give information about inconsistency, tautology, and possible simplifications.
We use different constraint domains which are mapped to SQL types, and propose them to cooperate for improving accuracy.
Our approach leverages a deductive system that includes SQL and Datalog, and we present an implementation in this system which is currently being tested in classroom, showing its advantages and differences with respect to other approaches, as well as some performance data.
This paper is under consideration for acceptance in TPLP.
\end{abstract}

  \begin{keywords}
    Constraint Logic Programming, SQL, Semantic Checking, Datalog Educational System
  \end{keywords}

\input{01intro}
\input{02sqltodatalog}
\input{03datalogtoclp}
\input{04systemimplementation}
\input{05relatedwork}
\input{06conclusions}

\bibliographystyle{acmtrans}
%\bibliography{biblio}
\input{iclp2019.bbl}
\end{document}

% end of new_TLP2egui.tex
