\section{Additional Proofs}
\label{app:proofs}


\begin{proof}[Proof of Lemma 1]
    If UAV $i$ was not recalculated in the previous round, then $|\mathcal{D}_{iw}| = 1$. If the CU received the trajectory metadata, it directly knows the trajectory UAV $i$ is following. If the metadata was not received due to message loss, since the database is not deprecated (it would have been marked otherwise), the CU still knows the trajectory from prior rounds.

    If UAV $i$ was recalculated in the previous round, then at Line~\ref{lst:line:deprecatedtwo} in Algorithm~\ref{alg:processmessages}, the database contains the trajectory UAV $i$ was following two rounds ago. After processing, it includes this trajectory and the new one calculated and transmitted in the last round. Depending on whether UAV $i$ received the new trajectory, it is following one of these two trajectories. Thus, the CU knows the possible trajectories UAV $i$ may be following.
\end{proof}

\begin{proof}[Proof of Lemma 2]
    For UAVs not recalculated in the last round, the intermediate databases $\tilde{\mathcal{D}}_{iv}(k)$ and $\tilde{\mathcal{D}}_{iw}(k)$ contain their actual trajectories (Lines~\ref{lst:line:metadatacompbegin}--\ref{lst:line:metadatacompend}, Lemma~\ref{col:information-tracker}). For UAVs recalculated in the last round, the databases contain their trajectories from the last or second-to-last round, depending on recalculations due to the event trigger. After updating $\tilde{\mathcal{D}}$, the newly calculated trajectories are added (Lines~\ref{lst:line:updateinformationtrackerbegin}--\ref{lst:line:updateinformationtrackerend}). The databases are not deprecated only if all new trajectories are received, ensuring $\mathcal{D}_{iw}(k) = \mathcal{D}_{iv}(k)$.
\end{proof}

% \begin{proof}[Proof of Lemma 1]
%     If UAV $i$ was not recalculated in the round before, we know that $|\mathcal{D}\ul{iw}| = 1$.
%     If the CU has received  the metadata of the trajectory, 
%     we directly know that this is the trajectory the UAV is following. 
%     If the CU has not received the metadata (because of message loss), this follows from the fact, that in at least one of the rounds before the metadata must have matched, otherwise the database would be deprecated. 
    
%     If UAV $i$ was recalculated in the round before, we know that at Line~\ref{lst:line:deprecatedtwo} in Algorithm~\ref{alg:processmessages}, the content of the database is the trajectory the UAV was planning to follow two rounds ago. 
%     At the end of the algorithm, this database contains this trajectory and the trajectory that was calculated and transmitted in the last round. 
%     One of these trajectories is the true trajectory, depending if UAV $i$ received the new trajectory or not.
% \end{proof}

% \begin{proof}[Proof of Lemma 2]
%     We know that the intermediate databases $\mathcal{\tilde{D}}\uli{iv}(k)$ and $\mathcal{\tilde{D}}\uli{iw}(k)$ contain the trajectories the UAVs are really following, if these UAVs were not recalculated in the last round ((Lines~\ref{lst:line:metadatacompbegin}--\ref{lst:line:metadatacompend}), Lemma~\ref{col:information-tracker}). 
%     For the UAVs that were recalculated in the last round, we know that the database contains the trajectories that the UAVs were following in in the last round (because of the event-trigger they were not recalculated in the second last round). 
%     For the ones that were recalculated, they contain the trajectories the UAVs were following in the second last round. 
%     After calculating $\tilde{D}$, the algorithm adds the newly calculated trajectories to the database (Lines~\ref{lst:line:updateinformationtrackerbegin}--\ref{lst:line:updateinformationtrackerend}). 
%     As the resulting databases are not deprecated only if all newly calculated trajectories are received $\mathcal{D}\ul{iw}(k) = \mathcal{D}\ul{iv}(k)$. 
% \end{proof}

\begin{proof}[Proof of Corrolary 1]
    As both UAVs are selected for computation, we know $|\mathcal{D}\uli{j}| = 1$.
    The corollary then follows from Lemma 1 in \citep{Graefe2022}.
\end{proof}
    
\begin{proof}[Proof of Lemma 3] 
    We know that because UAV $j$ was not recalculated $\tilde{p}\uli{j}(\cdot|k)=p\uli{j}(\cdot+T|k-1)\in\mathcal{D}\ul{j}(k-1)$ (Equation (\ref{eq:nottriggered})). 
    It is
    \begin{align}
        ||&\Theta^{-1}[\tilde{p}\uli{j}(hT\ul{c}+T|k)-\hat{p}\uli{i,w}(hT\ul{c}+T|k)]||\ul{2}\nonumber\\ 
        &=||n\uli{\mathrm{0}, ij}(hT\ul{c}+2T|k-1)||\ul{2}||\Theta^{-1}\nonumber\\
        &\opindent\times[\tilde{p}\uli{j}(hT\ul{c}+T|k)-\hat{p}\uli{i,w}(hT\ul{c}+T|k)]||\ul{2}\nonumber \\
        &\geq n\uli{\mathrm{0}, ij}(hT\ul{c}+2T|k-1)^T\Theta^{-1}\nonumber\\
        &\opindent\times[p\uli{j}(hT\ul{c}+T|k)- \hat{p}\uli{i,w}(hT\ul{c}+T|k)]\nonumber\\
        &= n\uli{\mathrm{0}, ij}(hT\ul{c}+2T|k-1)^T\Theta^{-1}\nonumber\\
        &\opindent\times[p\uli{j}(hT\ul{c}+2T|k-1)- \hat{p}\uli{i,w}(hT\ul{c}+T|k)]\nonumber\\
        &\geq \hat{d}\ul{min}
    \end{align}
\end{proof}
    

\begin{proof}[Proof of Lemma 4] 
Since no new entries are added to the databases, there exists a trajectory $\tilde{p}\uli{i}(\cdot+T|k-1)\in\mathcal{D}_{i}(k)$ with $\tilde{p}\uli{i}(\cdot|k-1)=\tilde{p}\uli{i}(\cdot+T|k)$ (same for $j$), and thus collision freeness follows directly.
\end{proof}