\section{Related Research} 
\mpp/MAPF has been widely studied in the field of robotics. 
% 
In the static or one-shot setting \cite{stern2019multi},  given a graph environment and a number of robots with each robot having a unique start position and a goal position,  the task is to find collision-free paths for all the robots from start to goal.
%  
It has been proven that solving one-shot \mpp optimally in terms of minimizing either makespan or sum of costs is NP-hard \cite{surynek2010optimization,yu2013structure}.
% 
Moreover, it is also NP-hard to approximate within any constant factor less than 4/3 if the solution makespan is to be minimized~\cite{ma2016multi}.
% 


Existing solvers for \mpp can be broadly categorized into \emph{reduction-based}, \emph{search-based}, and \emph{rule-based}.  


Reduction-based solvers reduce \mpp to other well-studied problems, such as ILP\cite{yu2016optimal}, SAT\cite{surynek2010optimization} and ASP\cite{erdem2013general}.
% 
These solvers are able to find optimal solutions and are efficient for small and dense instances.
% 
There are dividing-and-conquer heuristics for enhancing their scalability \cite{guo2021spatial,yu2016optimal} at the cost of optimality.
% 
Unfortunately, these reduction-based methods are still incapable of dealing with the extremely dense scenarios we study in this paper.

% or use search algorithms to search the joint space to find the optimal solution \cite{sharon2015conflict,sharon2013increasing}.
% 
Another more popular approach develops search-based algorithms for \mpp problems that can be viewed are high-sophisticated A* \cite{hart1968formal} variants. 
% 
Coupled A* \cite{silver2005cooperative}, ICTS \cite{sharon2013increasing}, and CBS \cite{sharon2015conflict} are optimal solvers and efficient on large maps but with sparse robots.
% 
ECBS \cite{barer2014suboptimal} is the bounded-suboptimal version of CBS with enhanced scalability and bounded suboptimality.
% 
The search-based algorithms rely heavily on the heuristic for reducing the number of node expansions, i.e., Number Of Conflicts (\noc) which is used in \ecbs. 
% 
In dense scenarios, since robots are strongly correlated, this heuristic is not enough since there are lots of nodes with the same \noc.
% 
As a result, the number of nodes needed to expand to find a solution for existing \cbs variants grows exponentially with respect to the robot density, even if there is only a small number of robots.
% 

Rule-based solvers are another class of suboptimal \mpp solvers.
% 
Prioritized planners \cite{silver2005cooperative, okumura2019priority} assign priorities to robots and low-priority robots avoid conflicts with high-priority robots by treating them as dynamic obstacles.
% 
This is efficient but can easily cause dead-lock issues in dense scenarios, which leads to a low success rate.
% 
Another class of rule-based solvers introduces motion primitives for swapping the position of robots, such as Push-And-Swap \cite{luna2011push} and Rubik Table \cite{szegedy2020rearrangement,guo2022sub,GuoFenYu22IROS}.
% 
They are polynomial-time algorithms and can even solve extremely dense instances, but the solution quality is far from optimal.
% 
DDM\cite{han2019ddm} resolves the inter-robot conflicts efficiently by utilizing the precomputed motion primitive within the $3\times 3$ sub-grid.
% 
It finds near-optimal solutions when the robot density is not high but has the same optimality issue in dense scenarios.
% 




