%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is a general template file for the LaTeX package SVJour3
% for Springer journals.          Springer Heidelberg 2010/09/16
%
% Copy it to a new file with a new name and use it as the basis
% for your article. Delete % signs as needed.
%
% This template includes a few options for different layouts and
% content for various journals. Please consult a previous issue of
% your journal as needed.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
\RequirePackage{fix-cm}
%
%\documentclass{svjour3}                     % onecolumn (standard format)
\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
%\documentclass[smallextended]{svjour3}       % onecolumn (second format)
%\documentclass[twocolumn]{svjour3}          % twocolumn
%
\smartqed  % flush right qed marks, e.g. at end of proof
%
\usepackage{graphicx}
\usepackage{verbatim}
\usepackage{afterpage}
%\usepackage[textwidth=55pt,textsize=small]{todonotes}
\usepackage{url}
%\usepackage{hyperref}
\usepackage{amsmath}
%\usepackage{xfrac}
\usepackage{enumerate}
%\usepackage{verbatim}
\usepackage[round]{natbib}
\usepackage{inputenc}
\usepackage{sidecap}
\usepackage{booktabs}
\usepackage{todonotes}
\usepackage{xfrac}
\usepackage{placeins}

%\usepackage{mathptmx}      % use Times fonts if available on your TeX system

\journalname{Swarm Intelligence}
%
\begin{document}
\sloppy

\title{Evolution of Swarm Robotics Systems with \\Novelty Search}

\author{Jorge Gomes \and Paulo Urbano \and \\Anders Lyhne Christensen}

\institute{J. Gomes \at
              LabMAg, FCUL \& Instituto de Telecomunica\c{c}\~oes, Lisbon, Portugal \\
              \email{jgomes@di.fc.ul.pt}
           \and
           P. Urbano \at
           	  LabMAg, FCUL, Lisbon, Portugal \\
              \email{pub@di.fc.ul.pt}
           \and
           A. L. Christensen \at
              Instituto Universit\'ario de Lisboa (ISCTE) \& Instituto de Telecomunica\c{c}\~oes, Lisbon, Portugal\\
           	  \email{anders.christensen@iscte.pt}
}

\date{Received: 2012 / Accepted: April 2013}

\maketitle

\begin{abstract}

Novelty search is a recent artificial evolution technique that challenges traditional evolutionary approaches. In novelty search, solutions are rewarded based on their novelty, rather than their quality with respect to a predefined objective. The lack of a predefined objective precludes premature convergence caused by a deceptive fitness function. In this paper, we apply novelty search combined with NEAT to the evolution of neural controllers for homogeneous swarms of robots. Our empirical study is conducted in simulation, and we use a common swarm robotics task -- aggregation, and a more challenging task -- sharing of an energy recharging station. Our results show that novelty search is unaffected by deception, is notably effective in bootstrapping the evolution, can find solutions with lower complexity than fitness-based evolution, and can find a broad diversity of solutions for the same task. Even in non-deceptive setups, novelty search achieves solution qualities similar to those obtained in traditional 
fitness-based evolution. Our study also encompasses variants of novelty search that work in concert with fitness-based evolution to combine the exploratory character of novelty search with the exploitatory character of objective-based evolution. We show that these variants can further improve the performance of novelty search. Overall, our study shows that novelty search is a promising alternative for the evolution of controllers for robotic swarms.

\keywords{Evolutionary robotics \and neuroevolution \and swarm robotics \and novelty search \and NEAT \and behavioural diversity \and deception}
\end{abstract}

% Content

\input{intro}
\input{aggregation}
\input{sharing}
\input{combination}
\input{conclusion}

\section*{Acknowledgements}

This research has been supported by Funda\c{c}\~{a}o para a Ci\^{e}ncia e a Tecnologia (FCT) grants PTDC/EEACRO/104658/2008, PEst-OE/EEI/LA0008/2011, and SFRH/BD/89095/2012. 

\section*{Supplemental Material}

Videos of the behaviours are available as online supplemental material and at the following URL: \url{http://home.iscte-iul.pt/~alcen/si2013}. The source code of the software used in the experiments can be found at: \url{https://github.com/jorgemcgomes/evosimbad}.


% Biblio
\bibliographystyle{abbrvnat}
\bibliography{journal}

\end{document}
