% \documentclass[Afour,sageh,times]{sagej}

\documentclass[jair,twoside,11pt,theapa]{article}
\usepackage{jair, theapa, rawfonts}

\jairheading{1}{1993}{1-15}{6/91}{9/91}
\ShortHeadings{Anytime Stochastic Task and Motion Policies}
{Shah and Srivastava}


\usepackage{moreverb,url}
\usepackage{amsmath}

\usepackage{graphicx}
\usepackage{stmaryrd}

% \usepackage[colorlinks,bookmarksopen,bookmarksnumbered,citecolor=blue,urlcolor=red,draft]{hyperref}
% \usepackage[colorlinks,bookmarksopen,bookmarksnumbered,citecolor=blue,urlcolor=red]{hyperref}
\usepackage{url}
\usepackage{cleveref}
\usepackage[inline,shortlabels]{enumitem}
\usepackage[ruled,vlined,linesnumbered]{algorithm2e}
\usepackage{makecell}
\usepackage{tikz}
% \usepackage{natbib}
\usepackage{amssymb}
\usepackage{siunitx}

\newcommand{\U}{\mathcal{U}\xspace}
\newcommand\M{{\cal M}}        % caligraphic Mß
\newcommand{\mysssection}[1]{\noindent\textbf{#1}\hspace{8pt}}
\newcommand{\set}[1]{\{#1 \}}
\newcommand{\?}{\raisebox{.5pt}{\textcircled{\raisebox{-.9pt} {{\small
          ?}}}}}
\newcommand{\abs}[1]{\left[ #1 \right] }
\newcommand{\Tau}{\mathcal{T}}
\newcommand{\Psym}{\mathcal{P}_\text{sym}}
\newcommand{\Ph}{\mathcal{P}_\text{h}}
\newcommand{\psym}{p_\text{sym}}
\newcommand{\ph}{p_\text{h}}
\newcommand{\Asym}{\mathcal{A}_\text{sym}}
\newcommand{\Ah}{\mathcal{A}_\text{h}}
\newcommand{\Am}{\mathcal{A}} 
\newcommand{\asym}{a_\text{sym}}
\newcommand{\ah}{a_\text{h}}
\newcommand{\Pm}{\mathcal{P}}
\newcommand{\Sm}{\mathcal{S}}
\newcommand{\X}{\mathcal{X}}
\newcommand{\C}{\mathcal{C}}
\newcommand{\citet}[1]{\citeauthor{#1}~\citeyear{#1}}
\newcommand{\inter}[1]{\llbracket #1 \rrbracket}


\usepackage{lipsum}

\newcommand\blfootnote[1]{%
  \begingroup
  \renewcommand\thefootnote{}\footnote{#1}%
  \addtocounter{footnote}{-1}%
  \endgroup
}

\newtheorem{example}{Example}
\newtheorem{proposition}{Proposition}
\newtheorem{definition}{Definition}
\newtheorem{lemma}{Lemma}
\newtheorem{theorem}{Theorem}
\newtheorem{proof}{Proof}
\usepackage{xcolor}
\usepackage{etoolbox}
\usepackage{caption}
% \captionsetup[figure]{font=footnotesize}
\usepackage{subcaption}
\providetoggle{full}


\newcommand\BibTeX{{\rmfamily B\kern-.05em \textsc{i\kern-.025em b}\kern-.08em
T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

\def\volumeyear{2021}


\setcounter{secnumdepth}{3}
% \hypersetup{draft}
\begin{document}

\title{An Anytime Hierarchical Approach for \\ Stochastic Task and Motion Planning}

% \author{Naman Shah\affilnum{1} and Siddharth Srivastava\affilnum{1}}
% \author{Naman Shah\affilnum{1} and Siddharth Srivastava\affilnum{1}}
% \affiliation{\affilnum{1}Arizona State University, Tempe, AZ}

% \corrauth{Naman Shah, 
% School of Computing and Augmented Intelligence (SCAI),
% Arizona State University,
% Tempe, AZ, 85281, USA.}
\author{\name Naman Shah \email namanshah@asu.edu \\
    \addr Arizona State University, \\ 699 S Mill Ave, 
    Tempe, AZ, USA, 85281 
    \AND 
    \name Siddharth Srivastava \email siddharths@asu.edu \\ 
    \addr Arizona State University, \\ 699 S Mill Ave,
    Tempe, AZ, USA, 85281 
}


\maketitle

\begin{abstract}
    In order to solve complex, long-horizon tasks, intelligent robots
    need to carry out high level, abstract planning and reasoning in
    conjunction with motion planning. However, abstract models are
    typically lossy and plans or policies computed using them can be
    inexecutable. These problems are exacerbated in 
    stochastic situations where the robot needs to reason about, and
    plan for multiple  contingencies. 
      
    We present a new approach for integrated task and
    motion planning in stochastic settings. In contrast to prior work in this
    direction, we show that our approach can effectively compute
    integrated task and motion policies whose branching structures
    encode agent behaviors that handle multiple execution-time contingencies. We
    prove that our algorithm is probabilistically complete and can
    compute feasible solution policies in an anytime fashion so that the
    probability of encountering an unresolved contingency decreases over
    time. Empirical results on a set of challenging  problems show the
    utility and scope of our method.
\end{abstract}

% \keywords{ Stochastic task and motion planning, State and entity abstraction, Mobile manipulation, Hierarchical planning }

\blfootnote{In submission}

% \footnote{In submission}

\input{introduction.tex}

\input{background.tex}

\input{related.tex}

% ~\newpage ~ \newpage

\input{atm.tex}


% \newpage
% ~ \newpage
\input{algo.tex}

\input{empirical.tex}


% ~ \newpage~ \newpage


% \input{problem.tex}

% \input{conclusion.tex}

\section*{Acknowledgements}
This work was supported in parts by the NSF under grants IIS 1844325, IIS 1909370, and OIA 1936997.

% ~ \newpage
% ~ \newpage
\input{reference.tex}

z

\end{document}
