%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%2345678901234567890123456789012345678901234567890123456789012345678901234567890
%        1         2         3         4         5         6         7         8

\documentclass[letterpaper, 10 pt, journal, twoside]{IEEEtran}  
% Comment this line out if you need a4paper

%\documentclass[a4paper, 10pt, conference]{ieeeconf}      
% Use this line for a4 paper

%\IEEEoverridecommandlockouts                              
% This command is only needed if you want to use the \thanks command

%\overrideIEEEmargins                                      
% Needed to meet printer requirements.

% See the \addtolength command later in the file to balance the column lengths
% on the last page of the document

% Paper headers 
\markboth{IEEE Robotics and Automation Letters. Preprint Version. Accepted December, 2016}
{Long \MakeLowercase{\textit{et al.}}: Deep-Learned Collision Avoidance Policy for Distributed Multi-Agent Navigation}  
% Use only for final RAL version

\usepackage{color}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tabularx}
\usepackage{subcaption}
\captionsetup{font=small}
\captionsetup[sub]{font=small}
\usepackage{url}
\usepackage{cite}

\DeclareMathOperator*{\argmin}{\arg\!\min}
\DeclareMathOperator{\sigmoid}{sigmoid}


\title{Deep-Learned Collision Avoidance Policy for Distributed Multi-Agent Navigation} %Use for final RAL version

% Make room for more info lines in the \author command  
\author{Pinxin Long, Wenxi Liu*, and Jia Pan*%
\thanks{Manuscript received: September, 10, 2016; Revised December, 6, 2016; Accepted December, 29, 2016. This paper was recommended for publication by Editor Nancy Amato upon evaluation of the Associate Editor and Reviewers' comments.
This work was supported by HKSAR
Research  Grants  Council  (RGC)  General  Research  Fund
(GRF), CityU 17204115, 21203216, and NSFC/RGC Joint Research Scheme CityU103/16 . Asterisk
indicates the corresponding author.}
\thanks{Pinxin Long is with Dorabot Inc., Shenzhen, China. This work was done while the author was at the City University of Hong Kong (e-mail: pinxinlong@gmail.com)}%
\thanks{*Wenxi Liu is with the Department of Computer Science, Fuzhou University, Fuzhou, China (e-mail: wenxi.liu@hotmail.com)}%
\thanks{*Jia Pan is with the Department of Mechanical and Biomedical Engineering, City University of Hong Kong, Hong Kong, China (e-mail: jiapan@cityu.edu.hk)}%
\thanks{Digital Object Identifier (DOI): see top of this page.}
}
%Use only for final RAL version. 


% \author{Pinxin Long \and Wenxi Liu \and Jia Pan % <-this % stops a space
% %\thanks{*This work was not supported by any organization}% <-this % stops a space
% \thanks{The authors are with the Department of Mechanical and Biomedical Engineering, the City University of Hong Kong.
%         %{\tt\small b.d.researcher@ieee.org}
%         }%
% }

\begin{document}
\maketitle
%\thispagestyle{empty}
%\pagestyle{empty}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
High-speed, low-latency obstacle avoidance that is insensitive to sensor noise is essential for enabling multiple decentralized robots to function reliably in cluttered and dynamic environments. While other distributed multi-agent collision avoidance systems exist, these systems require online geometric optimization where tedious parameter tuning and perfect sensing are necessary. 

We present a novel end-to-end framework to generate reactive collision avoidance policy for efficient distributed multi-agent navigation. Our method formulates an agent's navigation strategy as a deep neural network mapping from the observed noisy sensor measurements to the agent's steering commands in terms of movement velocity. We train the network on a large number of frames of collision avoidance data collected by repeatedly running a multi-agent simulator with different parameter settings. We validate the learned deep neural network policy in a set of simulated and real scenarios with noisy measurements and demonstrate that our method is able to generate a robust navigation strategy that is insensitive to imperfect sensing and works reliably in all situations. We also show that our method can be well generalized to scenarios that do not appear in our training data, including scenes with static obstacles and agents with different sizes. Videos are available at \url{https://sites.google.com/view/deepmaca}.

\end{abstract}

% Keywords appear just beneath the abstract. Use only for final RAL version.  
\begin{IEEEkeywords}
Collision Avoidance; Distributed Robot Systems; Deep Learning; Multi-Agent Navigation %Path Planning for Multiple Mobile Robots or Agents; Autonomous Vehicle Navigation; Learning and Adaptive Systems

\end{IEEEkeywords}

\input{intro}
\input{related}
\input{overview}
\input{method}
\input{experiment}
\input{conclusion}


{\small
\bibliographystyle{IEEEtran}
\bibliography{references}
}


\end{document}












