\section{Results and Conclusion}

Our algorithm was preliminarily tested through the mini-competition against 10 teams of participants wishing to take part in the AI Soccer international competition, organized by the AI World Cup committee, in conjunction with the WCG 2019 Xi'an AI Masters \cite{wcg}. 9 out of 10 algorithms were learning-based and only one algorithm was rule-based. However, the details of others' algorithms have not been made public. Table \ref{tb:result} summarizes the result of the preliminary mini-competition. Our team won against 7 teams, lost against 2 teams, and tied with one team, resulting in our team being placed second among the entire teams. After preliminary testing against 10 teams, at last, we participated in the AI Soccer international competition with 130 teams from 39 countries. We advanced to the round of 16. Our team name is CY95, and the recorded video of the round of 16 is available at \cite{Youtube}.

\begin{table}
\caption{Results of the preliminary mini-competition.}
\begin{center}
\begin{tabular}{ccc}
\hline\rule{0pt}{12pt}
\textbf{Opponent  }\hspace{5mm}  & \textbf{Score}\hspace{5mm}   & \textbf{Victory} \\ [2pt]
\hline
Ours vs Team 1               & 13:8                 & Win                  \\ 
Ours vs Team 2               & 10:8                 & Win                  \\ 
Ours vs Team 3               & 7:13                 & Lose                  \\ 
Ours vs Team 4               & 6:6                 & Tie                  \\
Ours vs Team 5               & 8:7                 & Win                  \\
Ours vs Team 6               & 5:1                 & Win                  \\ 
Ours vs Team 7               & 20:3                 & Win                  \\ 
Ours vs Team 8               & 23:6                 & Win                  \\ 
Ours vs Team 9               & 8:10                 & Lose                  \\ 
Ours vs Team 10               & 8:4                 & Win                  \\ \hline


\end{tabular}
\end{center}
\label{tb:result}
\end{table}
Deep Q-Network was applied for training our agents in AI Soccer. We implemented DQN to train each agent so that it can take proper actions in different situations. We set the state space and the action space and rewards optimized for the AI Soccer task in a creative own way, and our algorithm was able to successfully train the agents. The performance of our algorithm was proven by 10 matches against 10 teams. Our algorithm proved its performance by advancing to the round of 16 in the AI Soccer international competition among 130 teams from 39 countries, organized by the AI World Cup committee, in conjunction with the WCG 2019 Xi'an AI Masters by successfully applying DQN to AI Soccer.