% This is LLNCS.DEM the demonstration file of
% the LaTeX macro package from Springer-Verlag
% for Lecture Notes in Computer Science,
% version 2.4 for LaTeX2e as of 16. April 2010
%
\documentclass[a4paper]{llncs}
\usepackage{graphicx}
\usepackage{makeidx}  % allows for indexgeneration
\usepackage{url}
\usepackage{footnote}
%
\usepackage{etoolbox} % for "\patchcmd" macro
\usepackage{enumitem}
\makeatletter
\patchcmd{\ps@headings}{\rlap{\thepage}}{}{}{}
\patchcmd{\ps@headings}{\llap{\thepage}}{}{}{}
\makeatother
\pagestyle{headings} % reload the now-modified "headings" page style
%
\usepackage{hyperref}

\makeatletter
\newcommand{\printfnsymbol}[1]{%
  \textsuperscript{\@fnsymbol{#1}}%
}
\makeatother
\usepackage{mathtools}
\usepackage{amsmath}
\usepackage{lipsum}
\makeatletter
\def\blfootnote{\gdef\@thefnmark{}\@footnotetext}
\makeatother
\begin{document}
%
%\frontmatter          % for the preliminaries
%
%\pagestyle{headings}  % switches on printing of running heads
%\addtocmark{Hamiltonian Mechanics} % additional mark in the TOC

%\tableofcontents
%
\mainmatter              % start of the contributions
%
\title{Deep Q-Network for AI Soccer}
\blfootnote{This work was supported by the Institute for Information \& Communications Technology Planning and Evaluation (IITP) grant funded by the Korea government (MSIT) (No.2020-0-00440, Development of Artificial Intelligence Technology that Continuously Improves Itself as the Situation Changes in the Real World.}
%
\titlerunning{Hamiltonian Mechanics}  % abbreviated title (for running head)
%                                     also used for the TOC unless
%                                     \toctitle is used
%
\author{Curie Kim\inst{1}\thanks{These authors equally contributed to this work} \and Yewon Hwang\inst{2}\printfnsymbol{1} \and Jong-Hwan Kim\inst{2}}

%
%\authorrunning{Ivar Ekeland et al.} % abbreviated author list (for running head)
%
%%%% list of authors for the TOC (use if author list has to be modified)
%\tocauthor{Ivar Ekeland, Roger Temam, Jeffrey Dean, David Grove,
%Craig Chambers, Kim B. Bruce, and Elisa Bertino}
%
\institute{Samsung Electronics\\
%\email{curie.kim@samsung.com}\\
\and KAIST 
} 

\maketitle              % typeset the title of the contribution

\begin{abstract}

Reinforcement learning has shown an outstanding performance in the applications of games, particularly in Atari games as well as Go. Based on these successful examples, we attempt to apply one of the well-known reinforcement learning algorithms, Deep Q-Network, to the AI Soccer game. AI Soccer is a 5:5 robot soccer game where each participant develops an algorithm that controls five robots in a team to defeat the opponent participant. Deep Q-Network is designed to implement our original rewards, the state space, and the action space to train each agent so that it can take proper actions in different situations during the game. Our algorithm was able to successfully train the agents, and its performance was preliminarily proven through the mini-competition against 10 teams wishing to take part in the AI Soccer international competition. The competition was organized by the AI World Cup committee, in conjunction with the WCG 2019 Xi'an AI Masters. With our algorithm, we got the achievement of advancing to the round of 16 in this international competition with 130 teams from 39 countries.
\keywords{Reinforcement Learning, AI Soccer, Deep Q-Network}
\end{abstract}
%
\input{1.Introduction}
\input{2.RelatedWork}
\input{3.Method}
\input{4.Results}

%
% ---- Bibliography ----
%
\bibliographystyle{splncs}
\bibliography{reference} 

\end{document}
