% ;; -*- coding: iso-latin-1; TeX-PDF-mode: t; TeX-master: "main" -*-%
\pdfoutput=1 
\documentclass[orivec]{llncs}

\usepackage{epsfig}
\usepackage{xspace}
\usepackage{wrapfig}
\usepackage{listings}
\usepackage{latexsym,amssymb}
\usepackage{amsmath}
\usepackage{alltt}
\usepackage[all]{xy}
\usepackage{algorithm2e}
\usepackage{algorithmicx}
\usepackage{multirow}
\usepackage{color} 
\usepackage{graphics}
\usepackage{graphicx}
\usepackage[draft]{fixme}
\usepackage{booktabs}
\usepackage{bold-extra}
\usepackage{hyperref}
\usepackage{listings}
\lstset{
  columns=fullflexible,
  frame=Ltb,
  framerule=0pt,
  aboveskip=0mm,
  framextopmargin=10pt,
  framexbottommargin=0pt,
  framexleftmargin=0cm,
  framesep=0pt,
  rulesep=0pt,
  % 
  stringstyle=\footnotesize\ttfamily,
  showstringspaces = false,
  basicstyle=\small\sffamily,
  commentstyle=\color{black},
  keywordstyle=\small\bfseries,
  % 
  numbers=left,
  mathescape=true,
  numbersep=2pt,
  numberstyle=\tiny,
 % numberfirstline=true,
  firstnumber=last,
  breaklines=true,
  language=Java %,
%  morekeywords={if,then,else,while,do,return,await,block,get,cog,skip,release,begin,Int,Unit,Str,True,False} 
}

\lstdefinestyle{PrologStyle} {
  language=Prolog,
  %frame=Ltb,
  framerule=0pt,
  basicstyle=\footnotesize\ttfamily,
  commentstyle=\color{black},
  keywordstyle=\footnotesize\ttfamily\bfseries,
  stringstyle=\footnotesize\ttfamily,
  showstringspaces = false,
  escapechar=@,%   <-- To start latex commands
  mathescape=true,
  extendedchars=true,%
  lineskip=0ex,%
  framerule=0pt,
  numbersep=2pt,
  numberstyle=\tiny,
  deletekeywords={length,ef}, % jmr: I don't know wh\y!
  morekeywords={set_field,get_field,return,async,get,new_object},
}

\include{costa-defs}


% General commands
\newcommand{\tuple}[1]{\langle #1 \rangle}
\newcommand{\maxcard}{C^{max}}
\newcommand{\mincard}{C^{min}}
\newcommand{\initcontexts}[1]{\mathcal{I}^{#1}}
\newcommand{\inittasks}{\mathcal{T}_{ini}}
\newcommand{\classcard}[1]{|M_{C_{#1}}|}
%
% Commands for this paper
\newcommand{\buffer}{\mathit{loc}}
\newcommand{\queue}[0]{\C{Q}}
\newcommand{\microstepstar}[1]{\stackrel{#1}{\leadsto^*}}
\newcommand{\macrostep}[1]{\stackrel{#1}{\longrightarrow}}
\newcommand{\newheap}{\ensuremath{newheap}}
\newcommand{\C}[1]{{\cal #1}}
\newcommand{\rrderiv}{\leadsto}
\newcommand{\sepo}{\cdot}
\newcommand{\many}[1]{\overline{#1}}
\newcommand{\fut}{\mathit{fut}} 
\newcommand{\objset}{\ensuremath{\mathtt{Loc}}}
\newcommand{\futset}{\ensuremath{\mathtt{Fut}}}
\newcommand{\namemethod}{m}
\newcommand{\mapping}{l}
\newcommand{\heap}{h}
\newcommand{\dom}[0]{\ensuremath{\mathit{dom}}}
\newcommand{\tkset}{\ensuremath{\mathtt{T}}}
\newcommand{\future}{f}
\newcommand{\objid}[0]{\ensuremath{\mathit{o}}\xspace}
\newcommand{\Tkid}[0]{\ensuremath{\mathit{Tk}}\xspace}
\newcommand{\itable}[0]{\ensuremath{\mathit{IT}}\xspace}
\newcommand{\Objid}[0]{\ensuremath{\mathit{L}}\xspace}
\newcommand{\Futid}[0]{\ensuremath{\mathit{F}}\xspace}
\newcommand{\tkid}[0]{\ensuremath{\mathit{tk}}\xspace}
\newcommand{\timeid}[0]{\ensuremath{\mathit{t}}\xspace}
\newcommand{\lst}[1]{\lstinline!#1!}
\newcommand{\sst}[2]{\ensuremath{s(#1,#2)}\xspace}
\newcommand{\st}[4]{\ensuremath{s(#1,#2,#3,#4)}\xspace}
\newcommand{\rhotable}{\mbox{\emph{status}}}
\newcommand{\selectObject}{\ensuremath{\mathit{selectLoc}}\xspace}
\newcommand{\selectTask}{\ensuremath{\mathit{selectTask}}\xspace}
\newcommand{\Await}[0]{\ensuremath{\mbox{\bf \lstinline!await!}}\xspace}
\newcommand{\get}[1]{\ensuremath{#1.\mbox{\bf \lstinline!get!}}\xspace}
\newcommand{\Get}[1]{\ensuremath{\mbox{\bf \lstinline!get!}}\xspace}
\newcommand{\newb}{\ensuremath{\mbox{\lstinline!new!}}\xspace}
\newcommand{\ifte}{\mbox{\lstinline!if!}\xspace}
\newcommand{\iftethen}{{\ensuremath{\mbox{\lstinline!then!}}\xspace}}
\newcommand{\ifteelse}{{\ensuremath{\mbox{\lstinline!else!}}\xspace}}
\newcommand{\while}{\mbox{\lstinline!while!}\xspace}
\newcommand{\whilebody}{\mbox{\lstinline!do!}\xspace}
\newcommand{\return}{\mbox{\lstinline!return!}\xspace}
\newcommand{\await}[1]{\mbox{\bf \lstinline!await!}~#1?\xspace}
\newcommand{\returnval}[1]{\mbox{\lstinline!return #1!}\xspace}
\newcommand{\body}[1]{\ensuremath{\mathit{body}(#1)}}
\newcommand{\nil}{\mbox{\lstinline!null!}\xspace}
\newcommand{\ex}{E}
\newcommand{\extend}[1]{S}
\newcommand{\exec}{{\it exec}}
\newcommand{\block}[1]{\ensuremath{#1.\mbox{\lstinline!block!}}}
\newcommand{\anndep}[1]{\ensuremath{\xrightarrow{#1}}}
\newcommand{\tktkdep}[0]{\ensuremath{\rightarrow}}
\newcommand{\abstkid}[0]{\ensuremath{\mathit{tk}}\xspace}
\newcommand{\ppset}{\ensuremath{\mathcal{P}}}
\newcommand{\pp}[1]{\ensuremath{\mathit{pp}(#1)}}
\newcommand{\taskpp}[2]{\ensuremath{{#1}{:}{#2}}}
\newcommand{\edge}[3]{\ensuremath{#1 \stackrel{_{#3}}{\longrightarrow} #2}}
\newcommand{\absobjid}[0]{\ensuremath{\mathit{ob}}\xspace}
\newcommand{\gdexec}[1]{{\it exec_{#1}}}
\newcommand{\deadlock}[1]{{\textsf{deadlock}(#1)}}

% CLP OPERATIONS
\newcommand{\newobject}{\texttt{new\_object}}
\newcommand{\getfield}{\texttt{get\_field}}
\newcommand{\setfield}{\texttt{set\_field}}
\newcommand{\mstep}{\texttt{mstep}}
\newcommand{\async}{\texttt{async}}
\newcommand{\getclp}{\texttt{get}}
\newcommand{\returnclp}{\texttt{return}}

\newcommand{\deps}[0]{\ensuremath{G}}
\newcommand{\absdeps}[0]{\ensuremath{\mathcal{G}}}
\newcommand{\ptresult}[0]{\ensuremath{\mathcal{A}}}

% Controlling the spaces
% \renewcommand{\topfraction}{0.998}
% \renewcommand{\textfraction}{0.01}
% \renewcommand{\floatpagefraction}{0.998}
\newcommand{\secbeg}{\vspace*{-0cm}}%-.15
\newcommand{\secend}{\vspace*{-0cm}}%-.15
\newcommand{\subsecbeg}{\vspace*{0cm}}
\newcommand{\subsecend}{\vspace*{0cm}}


% Commands needed for the TPLP style
%\newtheorem{definition}{Definition} % [section]
%\newtheorem{example}{Example} % [section]
%\newtheorem{proposition}{Proposition} % [section]
%\newtheorem{theorem}{Theorem} % [section]

\pagestyle{plain}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\title{On the Generation of Initial Contexts for Effective Deadlock
  Detection\\ (Extended Abstract)\vspace{-.3cm}\thanks{This work was
    funded partially by the Spanish MINECO project
    TIN2015-69175-C4-2-R, and by the CM project S2013/ICE-3006.}}
% \title{Combining Static Analysis and Symbolic Execution for Deadlock
%   Detection\vspace{-.3cm}}
\author{\vspace{-.0cm}Elvira Albert \and Miguel G\'omez-Zamalloa \and Miguel Isabel}

\institute{
Complutense University of Madrid (UCM),  Spain
\vspace{-.1cm}}

%\pagerange{\pageref{firstpage}--\pageref{lastpage}}
%\volume{\textbf{10} (3):}
%\jdate{December 2009}
\setcounter{page}{1}
%\pubyear{2010}

\maketitle

\label{firstpage}

\input abstract

% \begin{keywords} Testing, Deadlock detection, Symbolic execution, Test case
%   generation, Verification, Deadlock analysis
% \end{keywords}

\section{Motivation}\label{sec:intro}
\input intro

\section{Asynchronous Programs}\label{sec:lang}
\input language

\section{Specifying and Generating Initial Contexts}
\label{sec:initialcontexts}
\input initial_contexts

\section{On Automatically Inferring Deadlock-Interfering Tasks}\label{sec:initialtasks}
% \section{On Automatically Inferring Interfering Tasks}\label{sec:initial-tasks}
  \input initial_tasks

% \section{Experimental Evaluation}\label{sec:experiments}

% \input experiments

\section{Conclusions and Related Work}\label{sec:concl-future-work}

 \input conclusions

% %\subsection*{Acknowledgements}

\bibliographystyle{plain}
\begin{thebibliography}{10}
\bibitem{DBLP:conf/hvc/AgarwalWS05}
R.~Agarwal, L.~Wang, and S.~D. Stoller.
\newblock {Detecting Potential Deadlocks with Static Analysis and Run-Time
  Monitoring}.
\newblock In {\em Conf. on Hardware and Software Verification and Testing},
  volume 3875 of {\em Lecture Notes in Computer Science}, pages 191--207.
  Springer, 2006.

\bibitem{AlbertGI17_techrep}
E.~Albert, M.~G\'omez-Zamalloa, and M.~Isabel.
\newblock Deadlock {G}uided {T}esting in {CLP}.
\newblock Technical report, 2017.
\newblock Available at
  \url{http://costa.ls.fi.upm.es/papers/costa/AlbertGI17tr.pdf}.

\bibitem{AlbertGI16b-short}
Elvira Albert, Miguel G\'omez-Zamalloa, and Miguel Isabel.
\newblock Combining {S}tatic {A}nalysis and {T}esting for {D}eadlock
  {D}etection.
\newblock In {\em Proc. of IFM'16}, volume 9681 of {\em LNCS}, pages 409--424.
  Springer, 2016.

\bibitem{DBLP:conf/icst/ChristakisGS13}
Maria Christakis, Alkis Gotovos, and Konstantinos~F. Sagonas.
\newblock {Systematic Testing for Detecting Concurrency Errors in Erlang
  Programs}.
\newblock In {\em Sixth {IEEE} International Conference on Software Testing,
  Verification and Validation, {ICST} 2013, Luxembourg, Luxembourg, March
  18-22, 2013}, pages 154--163. {IEEE} Computer Society, 2013.

\bibitem{deboer07esop-short}
F.~S. de~Boer, D.~Clarke, and E.~B. Johnsen.
\newblock A {C}omplete {G}uide to the {F}uture.
\newblock In {\em Proc. of ESOP'07}, volume 4421 of {\em LNCS}, pages 316--330.
  Springer, 2007.

\bibitem{flanagan95:futures}
C.~Flanagan and M.~Felleisen.
\newblock The semantics of future and its use in program optimization.
\newblock In {\em 22nd ACM SIGPLAN-SIGACT Symposium on Principles of
  Programming Languages}, 1995.

\bibitem{FloresAG13-short}
A.~Flores-Montoya, E.~Albert, and S.~Genaim.
\newblock May-{H}appen-in-{P}arallel based {D}eadlock {A}nalysis for
  {C}oncurrent {O}bjects.
\newblock In {\em FORTE'13}, LNCS 7892, pages 273--288. Springer, 2013.

\bibitem{GGLLW13}
E.~Giachino, C.A. Grazia, C.~Laneve, M.~Lienhardt, and P.~Wong.
\newblock {D}eadlock {A}nalysis of {C}oncurrent {O}bjects -- {T}heory and
  {P}ractice, 2013.

\bibitem{DBLP:conf/concur/GiachinoKL14}
Kobayashi~N. Giachino~E. and Laneve C.
\newblock Deadlock analysis of unbounded process networks.
\newblock In {\em {CONCUR} 2014, Rome, Italy, September 2-5, 2014.
  Proceedings}, pages 63--77, 2014.

\bibitem{DBLP:journals/sosym/GiachinoLL16}
Laneve~C. Giachino~E. and Lienhardt M.
\newblock A framework for deadlock detection in core {ABS}.
\newblock {\em Software and System Modeling}, 15(4):1013--1048, 2016.

\bibitem{DBLP:conf/sigsoft/JoshiNSG10}
P.~Joshi, M.~Naik, K.~Sen, and Gay D.
\newblock An effective dynamic analysis for detecting generalized deadlocks.
\newblock In {\em Proc. of FSE'10}, pages 327--336. {ACM}, 2010.

\bibitem{DBLP:conf/pldi/JoshiPSN09}
P.~Joshi, C.~Park, K.~Sen, and M.~Naik.
\newblock A randomized dynamic program analysis technique for detecting real
  deadlocks.
\newblock In {\em Proc. of PLDI'09}, pages 110--120. {ACM}, 2009.

\bibitem{lockout}
A.~Kheradmand, B.~Kasikci, and G.~Candea.
\newblock {Lockout: Efficient Testing for Deadlock Bugs}.
\newblock Technical report, 2013.
\newblock Available at \url{http://dslab.epfl.ch/pubs/lockout.pdf}.

\bibitem{DBLP:conf/pdd/MasticolaR91}
S.~P. Masticola and B.~G. Ryder.
\newblock A {M}odel of {A}da {P}rograms for {S}tatic {D}eadlock {D}etection in
  {P}olynomial {T}ime.
\newblock In {\em Parallel and Distributed Debugging}, pages 97--107. ACM,
  1991.

\bibitem{Milanova2005}
Ana Milanova, Atanas Rountev, and Barbara~G. Ryder.
\newblock Parameterized {O}bject {S}ensitivity for {P}oints-to {A}nalysis for
  {J}ava.
\newblock {\em ACM Transactions on Software Engineering Methodology}, 14:1--41,
  2005.

\bibitem{DBLP:journals/tocs/SavageBNSA97}
S.~Savage, M.~Burrows, G.~Nelson, P.~Sobalvarro, and T.~E. Anderson.
\newblock Eraser: {A} dynamic data race detector for multithreaded programs.
\newblock {\em {ACM} Trans. Comput. Syst.}, 15(4):391--411, 1997.

\bibitem{DBLP:conf/fase/SenA06}
Koushik Sen and Gul Agha.
\newblock Automated {S}ystematic {T}esting of {O}pen {D}istributed {P}rograms.
\newblock In Luciano Baresi and Reiko Heckel, editors, {\em Fundamental
  Approaches to Software Engineering, 9th International Conference, {FASE}
  2006, Held as Part of the Joint European Conferences on Theory and Practice
  of Software, {ETAPS} 2006, Vienna, Austria, March 27-28, 2006, Proceedings},
  volume 3922 of {\em Lecture Notes in Computer Science}, pages 339--356.
  Springer, 2006.


\end{thebibliography}
% \newpage
% \input proofs

\end{document}
