\beginbass
%
In \Cref{sec:original_sub} we pointed out the \emph{safety}-preserving
property of \Cref{prop:safe_sub}.
Indeed, the two substitutions proposed in \Cref{ex:original_sub}
do not break the correctness of the communication between the entities.
%
However, the subtyping relation introduced by \cite{GayHole05}
can break the \emph{liveness} of the session on which it is applied.


\begin{example}
	\label{ex:unfair_sub}
	Consider the session types $\S_b$ and $\S_s$ from \Cref{ex:bin_bsc}. 
	The following judgment can be derived
	\[
	\begin{array}{lclclcl}
		\S_b & = 			& \Out\tadd.\S_b \choice \Out\tpay.\End[\Out]
				 & \usubt & \S_b^\infty
				 & = 			& \Out\tadd.\S_b^\infty
	\end{array}
	\]
	Let us look at the infinite derivation tree
	\[
	\begin{prooftree}
		\[
			\[
				\vdots
				\justifies
				\S_b \usubt \S_b^\infty
				\using\refrule{us-tag-out}
			\]
			\justifies
			\S_b \usubt \S_b^\infty
			\using\refrule{us-tag-out}
		\]
		\justifies
		\Out\tadd.\S_b \choice \Out\tpay.\End[\Out] \usubt
		\Out\tadd.\S_b^\infty
		\using\refrule{us-tag-out}
	\end{prooftree}
	\]
	As a consequence, \actor{buyer} can be replaced with
	\actor{buyer$_\infty$} behaving as $\S_b^\infty$
	by using \Cref{prop:safe_sub} (it only $\tadd$s items). 
	No matter how it reduces,
	the \actor{buyer$_\infty$} will never $\tpay$ the amount and the
	session will never terminate. Moreover, the only run of the
	session is infinite and \emph{fair} since it does not contain
	any weakly terminating state.
	%
	This example applies to \Cref{ex:bsc_multi} as well.
	%
	\eoe
\end{example}

Intuitively, the problem of the subtyping we investigated so far lies
in the contravariance of the output rule \refrule{us-tag-out}.
When such rule is applied, some branches are cut and it might happen
that all those branches leading to termination are removed. 
This is what happens in \Cref{ex:unfair_sub}.
Hence, the subtyping of \cite{GayHole05} must be refined
to preserve the termination property of the session.
