In this work, we formulate a decentralized intelligent decision-making framework for multi-agent teams to learn efficient task allocation strategies with load management through deep reinforcement learning. The proposed framework (HTLM Dec-POMDP) models idling as an option of allocation decision and encourages idling behaviors to conserve task load and available resources by customizing individual reward functions based on agent preferences. Training multi-agent teams with the HTLM Dec-POMDP framework allows agents to reduce task load without compromising the operation effectiveness and provides the opportunity to investigate team member selection, team resilience, and precaution preparation. Results show that properly defined reward functions can achieve load reduction and resource conservation while maintaining team performance. A metric for agent importance is defined to measure agent significance within the team and to suggest team formation and reliability.

The proposed method serves as an incentive for developing intelligent multi-agent task allocation systems with the consideration of load management, which could be beneficial for designing management-level strategies in complex operations for human-autonomy teams. The method could potentially suggest decisions to human agents in real practices without being overloaded. %Especially when the trained decisions are suggested to human agents in real practices.
In large-scale problems, as more tasks and agents are involved, a logistic of subteam formation and a hierarchical task planning method are desired to enhance computational efficiency. Moreover, the study of agent importance demonstrates asymmetric behaviors in collaboration with respect to capabilities, which potentially opens the discussion on studying collaborative teaming behaviors in the future.
