\vspace{5pt}
\PlanTriple{%
  Do The Importance of Being Icelandic and The Five Obstructions belong to different film genres?
}{%
  1. Use the \texttt{ask\_search\_agent} to determine the genre of ``The Importance of Being Icelandic'' by querying a reliable film database or source. Provide the query: ``What is the primary film genre of `The Importance of Being Icelandic'? Provide the genre name.''\\  
  2. Use the \texttt{ask\_search\_agent} again to determine the genre of ``The Five Obstructions'' with the query: ``What is the primary film genre of `The Five Obstructions'? Provide the genre name.''\\  
  3. Compare the two genre names obtained from the searches. If they are distinct, conclude that the films belong to different genres; otherwise, state they belong to the same genre.
}{%
  1. Use \texttt{ask\_search\_agent} to determine the primary film genre of ``The Importance of Being Icelandic'' by querying a reliable source like IMDb or Wikipedia. Provide \texttt{output\_content} as the genre name.\\  
  2. Use \texttt{ask\_search\_agent} to determine the primary film genre of ``The Five Obstructions'' using the same method. Provide \texttt{output\_content} as the genre name.\\ 
  3. Compare the two genre names obtained from the searches.\\  
  4. Use \texttt{final\_answer} to state whether the films belong to different genres based on the comparison.  
}{%
  Improved tool and argument specification, provides (additional) trusted sources for search
}\label{ex:genres}

\newpage
\PlanTriple{%
  According to Google Finance, when was the first year the Apple stock went above \$50 (without adjusting for stock split)?%
}{%
1. Use the \texttt{ask\_search\_agent} to query Google Finance for the first date when Apple's stock (AAPL) exceeded \$50 without adjusting for stock splits. Specify the query as: ``According to Google Finance, what was the first date Apple's stock (AAPL) went above \$50 without adjusting for stock splits? Provide the date.''\\
2. Extract the year from the identified date.\\
3. Verify the result by cross-checking Apple's stock split history to ensure the price threshold is unadjusted.\\  
4. Use the \texttt{final\_answer} tool to confirm the first year. 
}{%
  1. Use \texttt{ask\_search\_agent} to query Google Finance for the earliest date Apple's stock (AAPL) exceeded \$50 **without adjusting for stock splits**. Query: ``According to Google Finance, what was the first date Apple's stock (AAPL) closed above \$50 without adjusting for stock splits? Provide the date.''\\  
  2. Extract the year from the retrieved date.\\  
  3. Use \texttt{ask\_search\_agent} to confirm Apple's stock split history to ensure the identified date is **pre-split** (e.g., check split dates and ratios). Query: ``When did Apple (AAPL) undergo stock splits? Provide split dates and ratios.''\\ 
  4. Cross-reference the split dates with the retrieved date to verify it is unadjusted.\\  
  5. Use \texttt{final\_answer} to submit the confirmed year.
}{%
  Improved tool and argument specification, intermediate cross-reference/consistency checks
}\label{ex:apple}

\vspace{15pt}
\PlanTriple{%
  How many pages of the 2023 IPCC report (85 pages version) mention nuclear energy?
}{%
  1. Use \texttt{ask\_search\_agent} to search for the 2023 IPCC report's 85-page version text, specifying the need for the full content to analyze mentions of nuclear energy. Provide the query: ``What is the full text of the 2023 IPCC report (85 pages version)? Provide the complete document content.''\\  
  2. Use \texttt{inspect\_file\_as\_text} to analyze the retrieved report text (assuming the search provides a file path or URL) and identify all instances of terms related to nuclear energy (e.g., ``nuclear energy,'' ``nuclear power,'' ``nuclear fission'').\\  
  3. Count the unique pages containing these terms from the inspected text.\\  
  4. Use \texttt{final\_answer} to report the total number of pages mentioning nuclear energy.  
}{%
  1. Use \texttt{ask\_search\_agent} to locate the official 2023 IPCC report (85 pages version) and retrieve its full text or a downloadable PDF link from the IPCC website (https://www.ipcc.ch/). Provide the query: ``Where can I access the full text of the 2023 IPCC report (85 pages version)? Provide a direct download link.''\\
  2. Use \texttt{inspect\_file\_as\_text} to analyze the retrieved report text (via the provided link) and identify all instances of terms related to nuclear energy (e.g., ``nuclear energy,'' ``nuclear power,'' ``nuclear fission'').\\  
  3. Count the number of unique pages containing these terms, ensuring no duplicates.\\  
  4. Use \texttt{final\_answer} to submit the total count of pages mentioning nuclear energy. 
}{%
  Provides (additional) trusted sources for search
}\label{ex:nuclear}

\newpage
\vspace*{1pt}
\PlanTriple{%
  Who was the director of Chinese Coffee?
}{%
  Use \texttt{ask\_search\_agent} to search for ``Who is the director of the movie Chinese Coffee? Provide the name.'' on IMDb (https://www.imdb.com).\\  
  Extract the director's name from the search result.\\  
  Use \texttt{final\_answer} to provide the identified director's name.
}{%
  1. Use \texttt{ask\_search\_agent} to search for ``Who directed the movie Chinese Coffee?'' and request the output to provide the director's name.\\
  2. Analyze the detailed search results to confirm the director's identity from reliable sources (e.g., IMDb, Wikipedia).\\  
  3. Cross-check for title variations or potential ambiguities (e.g., ``Chinese Coffee'' vs. similar titles) in the search results.\\  
  4. Use \texttt{final\_answer} to provide the confirmed director's name.
}{%
  Provides (additional) trusted sources for search, intermediate cross-reference/consistency checks, clearer/more structured layout
}\label{ex:coffee}
\vspace{7.5pt}