\textcolor{darkgray}{\small{\textit{Read these instructions very carefully. Only after you have understood them well, navigate to the tasks in the next tab.\\
\\
\textbfrm{Goal}\\
\\
The goal of this annotation exercise is to label how much time it will take a human (not an LLM) to solve a given question.\\
\\
You will be provided with questions and you will need to solve each with web searches, using Google or Bing.\\
\\
You will need to use a stopwatch to measure your task completion time.\\
\\
Task completion time must be reported in the format <HH hours MM minutes SS seconds>, for example, 25 seconds would be written as <00 hours 00 minutes 25 seconds> . DO NOT REPORT MILLISECONDS, EVEN IF YOUR STOPWATCH SHOWS THEM.\\
\\
BE FAST: We are trying to measure a human’s *BEST* completion time, so please complete the task (correctly) as quickly as you can. While for most questions you will likely need web search, it is fine not to use it if you already know the answer. For some tasks, it is likely that you will need multiple, in-depth web searches.\\ 
\\
It is assumed that the search engine is already open in a tab. To avoid wasting time unnecessarily, please arrange the windows on your screen so that you can see both the question and the search engine side by side at the same time.\\
\\
Solve the task by following these steps:\\
\\
- Step 1: Read the question first, slowly and carefully.\\
- Step 2: Start the stopwatch.\\
- Step 3: Text can be copy-pasted to the search engine directly from the question. Indeed, for most questions this is advisable as it can save time. As soon as the answer to the question is found, stop the stopwatch (i.e., do not wait to type the answer) and record the completion time.\\
- Step 4: Provide the answer and the task completion time (as per the stopwatch).\\ 
\\
Note: You are allowed to read the question directly from the AI-generated summary at the top of the search engine page, if this is given. However, you are not allowed to copy-paste the question into an LLM chat interface. Use Google or Bing search.\\
\\
\textbfrm{Examples:}\\
\\
Question:\\
What is Miley Cyrus' occupation?\\
\\
Completion Time: 00 hours 00 minutes 04 seconds\\
Your Answer: Singer, songwriter, actress\\
\\
—\\
\\
Question:\\
Which came out first, Titanic or Clueless?\\
\\
Completion Time: 00 hours 00 minutes 17 seconds\\
Your Answer: Clueless}}}