\documentclass[11pt]{article}
%
\usepackage{graphicx}
\usepackage{fix-cm}
%
\usepackage{mathptmx}      % use Times fonts if available on your TeX system
%
% insert here the call for the packages your document requires
%\usepackage{latexsym}
% etc.
\usepackage{lp,graphicx,etoolbox}
\usepackage{amsmath, amssymb}
\usepackage{subfig,url}

\usepackage[noline,noend,linesnumberedhidden,boxed]{algorithm2e}
\DontPrintSemicolon
\SetArgSty{textnormal}
\SetAlCapSkip{1ex}
\SetAlgoCaptionLayout{centerline}



% 0.0in to center
\setlength{\topmargin}{-.5in}
\setlength{\textwidth}{6.5in}
\setlength{\oddsidemargin}{0.0in} \setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
%\setlength{\parskip}{\medskipamount}
\setlength{\marginparwidth}{1.2in}
%\renewcommand{\baselinestretch}{1.3}


\newcommand{\qed}{\rule{7pt}{7pt}}
%\newcommand{\proofof}[1]{\medskip\par\noindent{\sl Proof of #1}:\enspace}
\newcommand{\proofof}[1]{\smallskip\par\noindent{\sl Proof of #1}:\enspace}
\newenvironment{proof}{\noindent {\it Proof\/}:}{$\qed$ \medskip}
 \newcommand{\set}[1]{\{ #1 \}}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{conjecture}{Conjecture}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{fact}[theorem]{Fact}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{claim}[theorem]{Claim}
\newtheorem{prop}[theorem]{Proposition}







%%%%%
\newcommand{\argmin}{\hbox{argmin\,}}
\def\({\left(}
\def\){\right)}
\newcommand{\OPT}{\mbox{OPT}}
\newcommand{\mqed}{}
\newlength{\fixSUBT}
\settowidth{\fixSUBT}{\,}
\newcommand{\SUBT}{\ensuremath{SU\hspace*{-\fixSUBT}BT}}

\newtoggle{abs}
\toggletrue{abs}


\begin{document}

\title{On the Integrality Gap of the Subtour LP for the 1,2-TSP\thanks{A preliminary version of this paper appeared in LATIN 2012: Theoretical Informatics \cite{QianSWvZ11}. Some results in the current paper are stronger, using the same techniques as in~\cite{QianSWvZ11}.
The first author was supported in part by NSF grant CCF-1115256.  This work was carried out in part while the third author was on sabbatical at TU Berlin, and the fourth author was at Max-Planck-Institut f\"ur Informatik in Saarbr\"ucken, Germany.
The third author was supported in part by the Berlin Mathematical School, the Alexander von Humboldt Foundation, and NSF grant CCF-1115256.}
}

%\titlerunning{Short form of title}        % if too long for running head


\author{Jiawei Qian\thanks{Address: Bank of America Merrill Lynch,
Chicago, IL, 60661, USA.   Email: {\tt jq35@cornell.edu}.  Supported in part by NSF grant CCF-0830519.}
\and Frans Schalekamp\thanks{Address: Department of Mathematics, College of William and Mary, Williamsburg, VA 23185, USA. Email:{\tt frans@wm.edu}}
\and David P.\ Williamson\thanks{Address: School
of Operations Research and Information Engineering, Cornell
University, Ithaca, NY 14853, USA.  Email: {\tt dpw@cs.cornell.edu}.  This work was carried out while the author was on sabbatical at TU Berlin.
Supported in part by the Berlin Mathematical School, the Alexander von Humboldt Foundation, and NSF grant CCF-1115256.}
\and Anke van Zuylen
\thanks{Address: Department of Mathematics, College of William and Mary, Williamsburg, VA 23185, USA. Email:{\tt anke@wm.edu}}}

\date{}
\maketitle

\newtheorem{conj}{Conjecture}


\begin{abstract}
In this paper, we study the integrality gap of the subtour LP relaxation for the traveling salesman problem in the special case when all edge costs are either 1 or 2. For the general case of symmetric costs that obey triangle inequality, a famous conjecture is that the integrality gap is 4/3. Little progress towards resolving this conjecture has been made in thirty years.
We conjecture that when all edge costs $c_{ij}\in \{1,2\}$, the integrality gap is $10/9$. We show that this conjecture is true when the optimal subtour LP solution has a certain structure. Under a weaker assumption, which is an analog of a recent conjecture by Schalekamp, Williamson and van Zuylen, we show that the integrality gap is at most $7/6$. When we do not make any assumptions on the structure of the optimal subtour LP solution, we can show that integrality gap is at most $5/4$; this is the first bound on the integrality gap of the subtour LP strictly less than $4/3$ known for an interesting special case of the TSP.  We show computationally that the integrality gap is at most $10/9$ for all instances with at most 12 cities.
%\keywords{Traveling Salesman Problem \and Subtour elimination \and Linear programming \and Integrality gap}
% \PACS{PACS code1 \and PACS code2 \and more}
% \subclass{MSC code1 \and MSC code2 \and more}
%\subclass{90C05  	Linear programming, 90C27  	Combinatorial optimization, 05C70 Factorization, matching, covering and packing}
\end{abstract}

\input{intro}
\input{12tsp_v2}
\input{computation}
\input{conclusion}


\subsection*{Acknowledgements}
We thank Sylvia Boyd for useful and encouraging discussions.
We thank two anonymous referees for helpful comments and suggestions.


% BibTeX users please use one of
%\bibliographystyle{spbasic}      % basic style, author-year citations
\bibliographystyle{spmpsci}      % mathematics and physical sciences
%\bibliographystyle{spphys}       % APS-like style for physics
\bibliography{subtour}
\appendix
\input{appendix2arxiv}


\end{document}

