\textbf{ARC} \cite{clark2018thinksolvedquestionanswering}:\\
\noindent
%\textit{id:} Mercury\_SC\_415702\\
\textit{Question:} George wants to warm his hands quickly by rubbing them. Which skin surface will produce the most heat?\\
%\textit{Choices:} \{ "text": [ "dry palms", "wet palms", "palms covered with oil", "palms covered with lotion" ], "label": [ "A", "B", "C", "D" ] \}\\
\textit{Choice A:} dry palms \\
\textit{Choice B:} wet palms \\
\textit{Choice C:} palms covered with oil \\
\textit{Choice D:} palms covered with lotion \\
\textit{Answer Key:} A

\noindent
Example Source: \href{https://huggingface.co/datasets/allenai/ai2_arc/viewer/ARC-Challenge/train?row=0}{[link]}

\vspace{10pt}
\noindent
\textbf{Belebele} \cite{bandarkar2023belebele}:\\
\noindent
\textit{Passage:} Many paleontologists today believe that one group of dinosaurs survived and is alive today. We call them birds. Many people don't think about them as dinosaurs because they have feathers and can fly. But there are a lot of things about birds that still look like a dinosaur. They have feet with scales and claws, they lay eggs, and they walk on their two back legs like a T-Rex.\\
\textit{Question:} Which of the following characteristics is not commonly associated with dinosaurs?\\
\textit{Choice 1:} Back-leg walking\\
\textit{Choice 2:} Feathers\\
\textit{Choice 3:} Egg laying\\
\textit{Choice 4:} Clawed feet\\
\textit{Answer:} Choice 2

\noindent
Example Source: \href{https://huggingface.co/datasets/facebook/belebele/viewer/eng_Latn/test?row=201}{[link]}

\vspace{10pt}
\noindent
\textbf{HellaSwag} \cite{zellers2019hellaswagmachinereallyfinish}:\\
\noindent
%\textit{ind:} 14, 
%\textit{Activity Label:} Wakeboarding\\
\textit{Context:} A cartoon animation video is shown with people wandering around and rockets being shot. two men\\
%\textit{Endings:}\\
\textit{Ending 1:} fight robots of evil and ends with a to be continued.\\
\textit{Ending 2:}  are then shown in closeups shooting a shot put.\\
\textit{Ending 3:}  push a child in a speedboat in the water.\\
\textit{Ending 4:}  look in the cameraman's eye and smile. \\
\textit{Answer:} Ending 1
%\textit{Source ID:} activitynet\_v-5KAycAQlC4

\noindent
Example Source: \href{https://raw.githubusercontent.com/rowanz/hellaswag/a29ff8e9a04bba4bd6588223785ce105328adc57/data/hellaswag_val.jsonl#:~:text=%7B%22ind%22%3A%20170%2C,%7D}{[link]}

\vspace{10pt}
\noindent
\textbf{LAMBADA (OpenAI)} \cite{paperno2016lambadadatasetwordprediction}:\\
\noindent
\textit{Context:} Now, they were opening cans of pork \& beans and eating them cold. As to why they didn't heat them up first, it took some prying but Lucas finally admitted that there had been a bit of an accident when they had used the stove and it had caught on fire. The ship was fine but they weren't sure about the stove.
%\textit{Test-set - row 28}

\noindent
Example Source: \href{https://huggingface.co/datasets/EleutherAI/lambada_openai/viewer/en/test?row=28}{[link]}

\vspace{10pt}
\noindent
\textbf{MMLU} \cite{hendrycks2021measuringmassivemultitasklanguage}:\\
\noindent
\textit{Question:} According to Moore’s “ideal utilitarianism,” the right action is the one that brings about the greatest amount of:\\
%\textit{Choices:} a) pleasure. b) happiness. c) good. d) virtue.\\
\textit{Choice A:} pleasure. \\
\textit{Choice B:} happiness. \\
\textit{Choice C:} good. \\
\textit{Choice D:} virtue. \\
\textit{Answer:} Choice C

\noindent
Example Source: \href{https://huggingface.co/datasets/alexandrainst/m_mmlu/viewer/en/train?row=2}{[link]}

\vspace{10pt}
\noindent
\textbf{MGSM Direct} \cite{shi2022languagemodelsmultilingualchainofthought}:\\
\noindent
\textit{Question:} Janet’s ducks lay 16 eggs per day. She eats three for breakfast every morning and bakes muffins for her friends every day with four. She sells the remainder at the farmers' market daily for \$2 per fresh duck egg. How much in dollars does she make every day at the farmers' market?\\
\textit{Answer:} 18

\noindent
Example Source: \href{https://github.com/google-research/url-nlp/blob/20e6cc665485b8370fdc724b52031f9673a98936/mgsm/mgsm_en.tsv#L1}{[link]}

\vspace{10pt}
\noindent
\textbf{MGSM Native CoT} \cite{shi2022languagemodelsmultilingualchainofthought}:\\
\noindent
\textit{Question:} Roger has 5 tennis balls. He buys 2 more cans of tennis balls. Each can has 3 tennis balls. How many tennis balls does he have now?\\
\textit{Step-by-Step Answer:} Roger started with 5 balls. 2 cans of 3 tennis balls each is 6 tennis balls. 5 + 6 = 11. The answer is 11.

\noindent
Example Source: \href{https://github.com/google-research/url-nlp/blob/20e6cc665485b8370fdc724b52031f9673a98936/mgsm/exemplars.py\#L356-L363}{[link]}

\vspace{10pt}
\noindent
\textbf{PAWS-X} \cite{pawsx2019emnlp}:\\
\noindent
%\textit{id:} 1\\
\textit{sentence1:} In Paris, in October 1560, he secretly met the English ambassador, Nicolas Throckmorton, asking him for a passport to return to England through Scotland.\\
\textit{sentence2:} In October 1560, he secretly met with the English ambassador, Nicolas Throckmorton, in Paris, and asked him for a passport to return to Scotland through England.\\
\textit{Label:} 0 (Not Paraphrased)

\noindent
Example Source: \href{https://huggingface.co/datasets/google-research-datasets/paws-x/viewer/en/train?row=0}{[link]}

\vspace{10pt}
\noindent
\textbf{TruthfulQA} \cite{lin-etal-2022-truthfulqa}:\\
\noindent
\textit{Question:} What is the smallest country in the world that is at least one square mile in area?\\
\textit{Choice 1}: Nauru is the smallest country in the world that is at least one square mile in area.\\
\textit{Choice 2}: The smallest country in the world that is at least one square mile in area is Vatican City.\\
\textit{Choice 3}: The smallest country in the world that is at least one square mile in area is Monaco. \\
\textit{Choice 4}: The smallest country in the world that is at least one square mile in area is the United States.\\
\textit{Answer:} Choice 1

\noindent
Example Source: \href{https://huggingface.co/datasets/truthfulqa/truthful_qa/viewer/multiple_choice/validation?row=0}{[link]}

\vspace{10pt}
\noindent
\textbf{XCOPA} \cite{ponti-etal-2020-xcopa}:\\
\noindent
\textit{Premise:} The girl found a bug in her cereal.\\
\textit{Question:} Result\\
\textit{Choice 1:} She poured milk in the bowl.\\
\textit{Choice 2:} She lost her appetite.

\noindent
Example Source: \href{https://web.archive.org/web/20221212001743im_/https://people.ict.usc.edu/~gordon/downloads/COPA-questions-dev.txt#:~:text=402%3A,appetite.}{[link]}

\vspace{10pt}
\noindent
\textbf{XNLI} \cite{conneau2018xnlievaluatingcrosslingualsentence}:\\
\noindent
\textit{Premise:} He started slowly back to the bunkhouse.\\
\textit{Hypothesis:} He returned slowly to the bunkhouse.\\
\textit{Label:} entailment

\noindent
Example Source: \href{https://huggingface.co/datasets/facebook/xnli/viewer/en/train?row=24}{[link]}

\vspace{10pt}
\noindent
\textbf{XStoryCloze} \cite{lin2022fewshotlearningmultilinguallanguage}:\\
\noindent
\textit{Context:} Karen was assigned a roommate her first year of college. Her roommate asked her to go to a nearby city for a concert. Karen agreed happily. The show was absolutely exhilarating.\\
\textit{Right Ending:} Karen became good friends with her roommate.\\
\textit{Wrong Ending:} Karen hated her roommate.

\noindent
Example Source: \href{https://cs.rochester.edu/nlp/rocstories/#:~:text=Karen,hated%20her%20roommate.}{[link]}

\vspace{10pt}
\noindent
\textbf{XWinograd} \cite{tikhonov-ryabinin-2021-heads}:\\
\noindent
\textit{Sentence:} The city councilmen refused the demonstrators a permit because \_ feared violence.\\
%\textit{Options:}\\
\textit{Option 1:} the demonstrators\\
\textit{Option 2:} The city councilmen\\
\textit{Answer:} Option 2

\noindent
Example Source: \href{https://huggingface.co/datasets/Muennighoff/xwinograd/viewer/en/test?row=0}{[link]}
