\beginalto
%
We have shown that generalized inference systems are an effective
framework for defining sound and complete proof systems of (some)
combined safety and liveness properties of (dependent) session types
(\Cref{def:wt,def:fcomp}), as well as of a liveness-preserving
subtyping relation (\Cref{def:fsub}).

\paragraph{Properties of Session Types.}
We think that this achievement is more than a coincidence.  One of
the fundamental results in model checking states that every property
can be expressed as the conjunction of a safety property and a
liveness
property \citep{AlpernSchneider85,AlpernScheider87,BaierKatoen08}.
The connections between safety and liveness on one side and
coinduction and induction on the other make \GISs appropriate for
characterizing combined safety and liveness properties.

\cite{Murgia19} studies a wide range of compliance relations
for processes and session types, showing that many of them are fixed
points of a functional operator, but not necessarily the least or
the greatest ones. In particular, he shows that 
\emph{progress compliance}, which is akin to our compliance (\Cref{def:comp}), is
a greatest fixed point and that \emph{should-testing compliance},
which is akin to our fair compliance (\Cref{def:fcomp}), is an
intermediate fixed point. These results are consistent with
\Cref{thm:compliance}.

\paragraph{Dependent Session Types.}
The first theories of dependent session types are those of
\cite{ToninhoCairesPfenning11} and \cite{GriffithGunter13}. These
works augment session types with binders, thus allowing for the
specification of message predicates.
%
\cite{ToninhoYoshida18} present a full calculus combining functions
and processes in which the structure of both types and processes may
depend on the content of messages. 
%
\cite{ThiemannVasconcelos20} propose a full model of functions and
processes enabling a simplified form of dependency whereby the
structure of types and processes may depend on labels and possibly
natural numbers. They introduce a conditional context extension
operator that prevents dependencies on linear values.

\cite{Zhou19} describes the theory and implementation of a
refinement session type system where the type of messages can be
refined by predicates that specify their properties and
relationships.

\paragraph{Formalizations of Session Type Systems.}
%
\cite{Thiemann19} gives the first mechanized proof of a calculus of
functions and sessions. His type system distinguishes between types
and session types, but only non-dependent pairs are considered.
%
\cite{HughesBradyVanderbauwhede19} describe an Idris EDSL where
dependent types enable reasoning on value dependencies between
exchanged messages.
%
\cite{ZalakainDardha20} give another Agda formalization of the
linear $\pi$-calculus. They focus exclusively on the process layer
and only consider channel types, using typing with
leftovers \citep{Allais17}.
%
\cite{RouvoetEtAl20} describe a technique inspired by separation
logic to specify and verify in Agda interpreters using linear
resources. Among the case studies they discuss is a linearly-typed
lambda calculus with primitives for session communications.