\documentclass[10pt,onecolumn,letterpaper]{article}
\usepackage{cvpr}
\usepackage[numbers,sort&compress]{natbib}
\usepackage{times}
\usepackage{eso-pic}

\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[breaklinks=true,bookmarks=false]{hyperref}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}[subsection]
\newtheorem{Def}{Definition}
\newtheorem{Cor}{Corollary}
\newtheorem{Exam}{Example}[subsection]
\newtheorem{Pro}{Proposition}[subsection]
\numberwithin{equation}{section}
\usepackage{datetime}

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{xcolor}         % colors

% \PassOptionsToPackage{options}{natbib}
\usepackage{graphicx}
\usepackage{amsmath} 
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{colortbl} 
\usepackage{tcolorbox}

% \usepackage[switch]{lineno}
% \usepackage{booktabs}
\usepackage{multirow}
\usepackage{array}
\usepackage{longtable}
\usepackage{adjustbox}
\usepackage{array}
\usepackage{lscape}
\usepackage{natbib}
\usepackage[a4paper,margin=1in,headheight=15pt,headsep=24pt]{geometry}
% \usepackage{scrtime}
% \usepackage{fancyhdr, blindtext}

\usepackage{fancyhdr}


% Optional math commands from https://github.com/goodfeli/dlbook_notation.
\input{math_commands.tex}

\usepackage{hyperref}
\usepackage{url}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{array}
\usepackage[table]{xcolor}
\usepackage{pifont}
\usepackage{subfigure}


% \usepackage{multibib}   %新增
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{amsmath,bm}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{multirow} 
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{setspace}
\usepackage{enumitem}


\cvprfinalcopy % *** Uncomment this line for the final submission
\def\cvprPaperID{****} % *** Enter the CVPR Paper ID here
\allowdisplaybreaks
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}
% Pages are numbered in submission mode, and unnumbered in camera-ready
%\ifcvprfinal\pagestyle{empty}\fi
% \setcounter{page}{1}

\begin{document}
% \pagestyle{fancy}
\lhead{}
\lfoot{\date{\today},\date{\currenttime}}
\rfoot{NGD for DL}

% \title{Instruction Learning Paradigms: A Dual Perspective on White-box and Black-box LLMs}
\title{IMAGINE: Integrating Multi-Agent System into One Model for Complex Reasoning and Planning
}
\author{
% Yanwei Ren, Liu Liu, Baosheng Yu, Jiayan Qiu, Quan Chen
\textbf{Xikai Zhang}$^{1}$\quad
\textbf{Bo Wang}$^{3}$\quad
\textbf{Likang Xiao}$^{1}$\quad
\textbf{Yongzhi Li}$^{3}$\quad\\
\textbf{Quan Chen}$^{3}$\quad
\textbf{Wenju Wu}$^{2,1}$\quad
\textbf{Liu Liu}$^{2,1*}$\\[0.5em]
$^1$Hangzhou International Innovation Institute, Beihang University\\
$^2$School of Artificial Intelligence, Beihang University\\
$^3$Kuaishou Technology
}
\maketitle
\begingroup
\renewcommand\thefootnote{*}
\footnotetext{Corresponding author: \texttt{liuliubh@buaa.edu.cn}}
\endgroup
% \thispagestyle{fancy}
\input{Main-Text/0abs}
\input{Main-Text/1Intr}
\input{Main-Text/2RelatedWork}
\input{Main-Text/3Met}
\input{Main-Text/4Exp}
\input{Main-Text/6Con}


% \section*{References}

\medskip

% \today
% {\small
%  \bibliographystyle{ieee}
%  \bibliography{main}
% }

\begin{thebibliography}{10}\itemsep=-1pt

\bibitem{chen2024survey}
S.~Chen, Y.~Liu, W.~Han, W.~Zhang, and T.~Liu.
\newblock A survey on llm-based multi-agent system: Recent advances and new frontiers in application.
\newblock {\em arXiv preprint arXiv:2412.17481}, 2024.

\bibitem{chen2024reprompt}
W.~Chen, S.~Koenig, and B.~Dilkina.
\newblock Reprompt: Planning by automatic prompt engineering for large language models agents.
\newblock {\em arXiv preprint arXiv:2406.11132}, 2024.

\bibitem{cheng2025revisiting}
Z.~Cheng, S.~Hao, T.~Liu, F.~Zhou, Y.~Xie, F.~Yao, Y.~Bian, Y.~Zhuang, N.~Dey, Y.~Zha, et~al.
\newblock Revisiting reinforcement learning for llm reasoning from a cross-domain perspective.
\newblock {\em arXiv preprint arXiv:2506.14965}, 2025.

\bibitem{choi2025atlas}
J.~Choi, J.~Yoon, J.~Chen, S.~Jha, and T.~Pfister.
\newblock Atlas: Constraints-aware multi-agent collaboration for real-world travel planning.
\newblock {\em arXiv preprint arXiv:2509.25586}, 2025.

\bibitem{de2008z3}
L.~De~Moura and N.~Bj{\o}rner.
\newblock Z3: An efficient smt solver.
\newblock In {\em International conference on Tools and Algorithms for the Construction and Analysis of Systems}, pages 337--340. Springer, 2008.

\bibitem{gandhi2025cognitive}
K.~Gandhi, A.~Chakravarthy, A.~Singh, N.~Lile, and N.~D. Goodman.
\newblock Cognitive behaviors that enable self-improving reasoners, or, four habits of highly effective stars.
\newblock {\em arXiv preprint arXiv:2503.01307}, 2025.

\bibitem{guo2025deepseek}
D.~Guo, D.~Yang, H.~Zhang, J.~Song, R.~Zhang, R.~Xu, Q.~Zhu, S.~Ma, P.~Wang, X.~Bi, et~al.
\newblock Deepseek-r1: Incentivizing reasoning capability in llms via reinforcement learning.
\newblock {\em arXiv preprint arXiv:2501.12948}, 2025.

\bibitem{guo2024large}
T.~Guo, X.~Chen, Y.~Wang, R.~Chang, S.~Pei, N.~V. Chawla, O.~Wiest, and X.~Zhang.
\newblock Large language model based multi-agents: A survey of progress and challenges.
\newblock {\em arXiv preprint arXiv:2402.01680}, 2024.

\bibitem{guo2025mirror}
Z.~Guo, B.~Xu, X.~Wang, and Z.~Mao.
\newblock Mirror: Multi-agent intra-and inter-reflection for optimized reasoning in tool learning.
\newblock {\em arXiv preprint arXiv:2505.20670}, 2025.

\bibitem{hao2024large}
Y.~Hao, Y.~Chen, Y.~Zhang, and C.~Fan.
\newblock Large language models can solve real-world planning rigorously with formal verification tools.
\newblock {\em arXiv preprint arXiv:2404.11891}, 2024.

\bibitem{hong2024metagpt}
S.~Hong, M.~Zhuge, J.~Chen, X.~Zheng, Y.~Cheng, C.~Zhang, J.~Wang, Z.~Wang, S.~K.~S. Yau, Z.~Lin, et~al.
\newblock Metagpt: Meta programming for a multi-agent collaborative framework.
\newblock International Conference on Learning Representations, ICLR, 2024.

\bibitem{jaech2024openai}
A.~Jaech, A.~Kalai, A.~Lerer, A.~Richardson, A.~El-Kishky, A.~Low, A.~Helyar, A.~Madry, A.~Beutel, A.~Carney, et~al.
\newblock Openai o1 system card.
\newblock {\em arXiv preprint arXiv:2412.16720}, 2024.

\bibitem{li2023camel}
G.~Li, H.~Hammoud, H.~Itani, D.~Khizbullin, and B.~Ghanem.
\newblock Camel: Communicative agents for" mind" exploration of large language model society.
\newblock {\em Advances in Neural Information Processing Systems}, 36:51991--52008, 2023.

\bibitem{liu2025symagent}
B.~Liu, J.~Zhang, F.~Lin, C.~Yang, M.~Peng, and W.~Yin.
\newblock Symagent: A neural-symbolic self-learning agent framework for complex reasoning over knowledge graphs.
\newblock In {\em Proceedings of the ACM on Web Conference 2025}, pages 98--108, 2025.

\bibitem{liu2025understanding}
Z.~Liu, C.~Chen, W.~Li, P.~Qi, T.~Pang, C.~Du, W.~S. Lee, and M.~Lin.
\newblock Understanding r1-zero-like training: A critical perspective.
\newblock {\em arXiv preprint arXiv:2503.20783}, 2025.

\bibitem{ou2025analyzing}
T.~Ou, S.~Vaduguru, and D.~Fried.
\newblock Analyzing information sharing and coordination in multi-agent planning.
\newblock {\em arXiv preprint arXiv:2508.12981}, 2025.

\bibitem{qian2025scaling}
C.~Qian, Z.~Xie, Y.~Wang, W.~Liu, K.~Zhu, H.~Xia, Y.~Dang, Z.~Du, W.~Chen, C.~Yang, Z.~Liu, and M.~Sun.
\newblock Scaling large language model-based multi-agent collaboration.
\newblock In {\em The Thirteenth International Conference on Learning Representations}, 2025.

\bibitem{qiao2025thematic}
T.~Qiao, C.~Walker, C.~Cunningham, and Y.~S. Koh.
\newblock Thematic-lm: a llm-based multi-agent system for large-scale thematic analysis.
\newblock In {\em Proceedings of the ACM on Web Conference 2025}, pages 649--658, 2025.

\bibitem{schulman2017proximal}
J.~Schulman, F.~Wolski, P.~Dhariwal, A.~Radford, and O.~Klimov.
\newblock Proximal policy optimization algorithms.
\newblock {\em arXiv preprint arXiv:1707.06347}, 2017.

\bibitem{shao2024deepseekmath}
Z.~Shao, P.~Wang, Q.~Zhu, R.~Xu, J.~Song, X.~Bi, H.~Zhang, M.~Zhang, Y.~Li, Y.~Wu, et~al.
\newblock Deepseekmath: Pushing the limits of mathematical reasoning in open language models.
\newblock {\em arXiv preprint arXiv:2402.03300}, 2024.

\bibitem{shinn2023reflexion}
N.~Shinn, F.~Cassano, A.~Gopinath, K.~Narasimhan, and S.~Yao.
\newblock Reflexion: Language agents with verbal reinforcement learning.
\newblock {\em Advances in Neural Information Processing Systems}, 36:8634--8652, 2023.

\bibitem{wang2025cooperative}
Z.~Wang, Z.~Zhao, Y.~Lyu, Z.~Chen, M.~de~Rijke, and Z.~Ren.
\newblock A cooperative multi-agent framework for zero-shot named entity recognition.
\newblock In {\em Proceedings of the ACM on Web Conference 2025}, pages 4183--4195, 2025.

\bibitem{wei2022chain}
J.~Wei, X.~Wang, D.~Schuurmans, M.~Bosma, F.~Xia, E.~Chi, Q.~V. Le, D.~Zhou, et~al.
\newblock Chain-of-thought prompting elicits reasoning in large language models.
\newblock {\em Advances in neural information processing systems}, 35:24824--24837, 2022.

\bibitem{10.1007/BF00992696}
R.~J. Williams.
\newblock Simple statistical gradient-following algorithms for connectionist reinforcement learning.
\newblock {\em Mach. Learn.}, 8(3–4):229–256, May 1992.

\bibitem{xie2024travelplanner}
J.~Xie, K.~Zhang, J.~Chen, T.~Zhu, R.~Lou, Y.~Tian, Y.~Xiao, and Y.~Su.
\newblock Travelplanner: A benchmark for real-world planning with language agents.
\newblock {\em arXiv preprint arXiv:2402.01622}, 2024.

\bibitem{xiong2025minimalist}
W.~Xiong, J.~Yao, Y.~Xu, B.~Pang, L.~Wang, D.~Sahoo, J.~Li, N.~Jiang, T.~Zhang, C.~Xiong, et~al.
\newblock A minimalist approach to llm reasoning: from rejection sampling to reinforce.
\newblock {\em arXiv preprint arXiv:2504.11343}, 2025.

\bibitem{yang2025plan}
D.~Yang, C.~Lu, Q.~Wang, X.~Ma, Y.~Gao, Y.~Hu, and H.~Zhao.
\newblock Plan your travel and travel with your plan: Wide-horizon planning and evaluation via llm.
\newblock {\em arXiv preprint arXiv:2506.12421}, 2025.

\bibitem{yu2025dapo}
Q.~Yu, Z.~Zhang, R.~Zhu, Y.~Yuan, X.~Zuo, Y.~Yue, W.~Dai, T.~Fan, G.~Liu, L.~Liu, et~al.
\newblock Dapo: An open-source llm reinforcement learning system at scale.
\newblock {\em arXiv preprint arXiv:2503.14476}, 2025.

\bibitem{yue2025does}
Y.~Yue, Z.~Chen, R.~Lu, A.~Zhao, Z.~Wang, S.~Song, and G.~Huang.
\newblock Does reinforcement learning really incentivize reasoning capacity in llms beyond the base model?
\newblock {\em arXiv preprint arXiv:2504.13837}, 2025.

\bibitem{zeeshan2025large}
T.~Zeeshan, A.~Kumar, S.~Pirttikangas, and S.~Tarkoma.
\newblock Large language model based multi-agent system augmented complex event processing pipeline for internet of multimedia things.
\newblock {\em arXiv preprint arXiv:2501.00906}, 2025.

\bibitem{zhang2024planning}
C.~Zhang, D.~G.~X. Deik, D.~Li, H.~Zhang, and Y.~Liu.
\newblock Planning with multi-constraints via collaborative language agents.
\newblock {\em arXiv preprint arXiv:2405.16510}, 2024.

\bibitem{zhang2025critique}
X.~Zhang, H.~Sun, Y.~Zhang, K.~Feng, C.~Lu, C.~Yang, and H.~Meng.
\newblock Critique-grpo: Advancing llm reasoning with natural language and numerical feedback.
\newblock {\em arXiv preprint arXiv:2506.03106}, 2025.

\bibitem{zhang2025swarmagentic}
Y.~Zhang, C.~Lin, S.~Tang, H.~Chen, S.~Zhou, Y.~Ma, and V.~Tresp.
\newblock Swarmagentic: Towards fully automated agentic system generation via swarm intelligence.
\newblock {\em arXiv preprint arXiv:2506.15672}, 2025.

\end{thebibliography}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \input{NList}
\end{document}
